### 2019-03-21 paper.tex
initial commit

\documentclass{article}
\title{The Epistemic Modal \emph{probable}: Qualitative and Quantitative Accounts}
\author{Conrad Friedrich \\ MCMP, LMU Munich \\ 1,337 words}
\date{\today}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{enumitem}
\usepackage{setspace}
% Used to scale \medcap
\usepackage{graphicx}
\usepackage[backend=biber,authordate,
ibidtracker=context,natbib,doi=false,isbn=false,url=false]{biblatex-chicago}

\addbibresource{/home/gilbert/Documents/bibliography/references.bib}

\newcommand*{\medcap}{\mathbin{\scalebox{1.5}{\ensuremath{\cap}}}}%
\renewcommand{\L}{\mathcal{L}}
\begin{document}

\onehalfspacing
\maketitle

\section{Introduction}
\section{Intensional Semantics}
Note that we don't need first order logic. 
Abstracted away from syntax, just look at the semantics.
\section{The Epistemic Modal \emph{probable}}
How is probable to be evaluated? MacFarlane's Solipcism.

To base the following discussions on a common language, we follow the definitions of a propositional language $\L$ by \textcite{harrison-trainor17_prefer} and \textcite{holliday13_measur}:
\[
\varphi ::= p ~|~ \neg \varphi ~|~ (\varphi \land \psi) ~|~ (\varphi \rightarrow \psi) ~|~ (\varphi \vee \psi) ~|~ (\varphi \succeq \psi) ~|~ \triangle\varphi 
\]
The intended readings for the Boolean operators are completely standard.
$\varphi \succeq \psi$ is to be read as `$\varphi$ is at least as likely as $\psi$', and $\triangle \varphi$ is to be read as `probably $\varphi$'.

We might leave uninterpreted some elements which don't figure prominently in the respective theory discussed at that moment.

\section{Kratzer's Analysis}

For \textcite{kratzer91_modal} epistemic modals like \emph{probably} are just a special case of a more general class of modal auxiliaries.
These can be epistemic (e.g. `Jockl must have been the murderer [in view of the available evidence]'), deontic (e.g. `Jockl must go to jail [in view of what the law provides]'), or circumstancial (e.g. `Jockl can lift the rock [given the weight of the rock and the conditions of Jockl's muscles, etc.]').
Further, there are teleological (in view of certain aims), bouletic (in view of certain wishes), and doxastic (in view of certain beliefs) modalities.
This list is by no means complete.

Kratzer postulates that modality is always relative to a certain kind of interpreting the modalities involved, following Peirce (cite).
She set out to formulate these different modalities in a common framework such that we'd only need to specify some parameters of the framework to determine the relevant modalities and give truth conditions for sentences involving modalities, while focussing on epistemic modals.

Kratzer is unhappy with what she calls the \emph{standard analysis} as is gives the wrong verdict in two salient scenarios.
--maybe also go through kratzer's examples which further motivate her decisions--maybe explain why we don't have an even easier definition.

Importantly, the account for modality needs to include graded modalities, of the following sort:
\begin{enumerate}[nosep,label=\alph*)]
  \item Michl must be the murderer.
  \item Michl is probably the murderer.
  \item There is a good possibility that Michl is the murderer.
  \item Michl might be the murderer.
\end{enumerate}
Here, the modalities are listed in decreasing strength, such that the intended reading is that a) implies b), b) implies c), and so forth. Note that is a qualitative approach to graded modals, as opposed to quantitative approaches, employing a scale structure in the semantics.

How does the semantics look like? For the basics: we assume a set $W$ of possible worlds, a set of propositions $P$ such that elements of $P$ are subsets of $W$, and that a proposition $p$ is true at $w$ iff $w \in p$. The crucial element in Kratzer's semantics is the \emph{conversational background}. It has two components.

The \emph{modal base} determines for every world the set of worlds which are epistemically accessible from it.
More formally, the modal base is a function $f: W \rightarrow \mathcal{P}(P)$\footnote{For finite $W$.} assigning each world $w$ a set of propositions.
The set of propositions $f(w)$ assigned to $w$ represents, in the epistemic case, what we know at $w$.
The set of epistemically accessible worlds then is $\bigcap f(w)$.

The \emph{ordering source} is a function $g: W \rightarrow \mathcal{P}(P)$ s.t. each $w$ is assigned a set of propositions $g(w)$ which interpreted as an \emph{ideal} (cf. \cite{lewis81_order_seman_premis_seman_count}). The ordering source induces an order $\leq_{g(w)}$ as follows for all $w,w' \in W$: 
\[
w \leq_A w' :\iff \{p: p\in A ~\&~ w' \in p\} \subseteq \{p: p\in A ~\&~ w \in p\}
\]
The intended reading is that $w$ is at least as close to the ideal represented by $A$ as $w'$ iff all the ideal propositions in $A$ which are true in $w'$ are also true in $w$.

From this, Kratzer defines a the semantics for a list of different expressions, like `good possibility', `possibility' and so on. For our purposes, it suffices to look at those definitions involved in defining the model `probable'.
\begin{align*}
 \llbracket \varphi \succeq \psi \rrbracket^{f,g,w} &= \forall u \in (\medcap f(w) \cap q) \exists v \in \medcapf(w): v \leq_{g(w)}u ~\&~ v \in \llbracket \varphi \rrbracket 
\end{align*}

\section{Yalcin and Lassiter's Probability Semantics}
Introduce the adequacy conditions V1-VXX etc.
\section{Holliday and Icard's Generalisation to Measure Semantics}
\section{Holliday and Icard's Unification of Preferential and Probabilistic Semantics}
\section{Conclusion}
What about the $\epsilon$-semantics (Adams, Pearl)? 
\nocite{hamblin59_modal_probab,holliday13_measur,harrison-trainor17_prefer,kratzer91_modal,lassiter10_gradab,yalcin10_probab_operat,kratzer98_seman}
 \printbibliography
\end{document}

### 2019-03-22 paper.tex
added adequacy conditions

@@
 \usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{stmaryrd}
@@
 \usepackage{graphicx}
+\usepackage{ebproof/ebproof}
+\usepackage{multicol}
+
 \usepackage[backend=biber,authordate,
@@
 \renewcommand{\L}{\mathcal{L}}
+\newcommand{\lb}{\llbracket}
+\newcommand{\rb}{\rrbracket}
 \begin{document}
@@
 \section{Introduction}
+
 \section{Intensional Semantics}
@@
 Abstracted away from syntax, just look at the semantics.
+NEAT summary in Ivano's script, Class 9, page 3/4
 \section{The Epistemic Modal \emph{probable}}
+Also show the need for expanding the standard intensional semantics!
 How is probable to be evaluated? MacFarlane's Solipcism.
@@
 The intended readings for the Boolean operators are completely standard.
-$\varphi \succeq \psi$ is to be read as `$\varphi$ is at least as likely as $\psi$', and $\triangle \varphi$ is to be read as `probably $\varphi$'.
-
+\begin{align*}
+  \varphi \succeq \psi &: \varphi \text{ is at least as likely as } \psi \\
+  \triangle \varphi &:\text{probably } \varphi.
+\end{align*}
 We might leave uninterpreted some elements which don't figure prominently in the respective theory discussed at that moment.
@@
 Note that is a qualitative approach to graded modals, as opposed to quantitative approaches, employing a scale structure in the semantics.
+\textcite{yalcin10_probab_operat} calls it a `relative likelihood' approach.
 
-How does the semantics look like?
-For the basics: we assume a set $W$ of possible worlds, a set of propositions $P$ such that elements of $P$ are subsets of $W$, and that a proposition $p$ is true at $w$ iff $w \in p$.
-The crucial element in Kratzer's semantics is the \emph{conversational background}.
+\subsection{Kratzer's Formal Setup}
+How do the semantics look like?
+we assume a set $W$ of possible worlds, a set of propositions $P$ such that elements of $P$ are subsets of $W$, and assume that a proposition $p$ is true at $w$ iff $w \in p$.
+The crucial element in Kratzer's semantics that distinguishes her account from most simple semantics via Kripke frames with an accessibility relation is the \emph{conversational background}.
 It has two components.
@@
 The \emph{modal base} determines for every world the set of worlds which are epistemically accessible from it.
-More formally, the modal base is a function $f: W \rightarrow \mathcal{P}(P)$\footnote{For finite $W$.} assigning each world $w$ a set of propositions.
+More formally, the modal base is a function $f: W \rightarrow \wp(P)$ assigning each world $w$ a set of propositions.
 The set of propositions $f(w)$ assigned to $w$ represents, in the epistemic case, what we know at $w$.
@@
 
-The \emph{ordering source} is a function $g: W \rightarrow \mathcal{P}(P)$ s.t.
+The \emph{ordering source} is a function $g: W \rightarrow \wp(P)$ s.t.
 each $w$ is assigned a set of propositions $g(w)$ which interpreted as an \emph{ideal} (cf.
 \cite{lewis81_order_seman_premis_seman_count}).
-The ordering source induces an order $\leq_{g(w)}$ as follows for all $w,w' \in W$:
+The ordering source induces a partial order (reflexive, antisymmetric and transitive) $\leq_{g(w)}$ as follows for all $w,w' \in W$:
 \[
-w \leq_A w' :\iff \{p: p\in A ~\&~ w' \in p\} \subseteq \{p: p\in A ~\&~ w \in p\}
+w \leq_{g(w)} w' :\iff \{p: p\in g(w) ~\&~ w' \in p\} \subseteq \{p: p\in  g(w) ~\&~ w \in p\}
 \]
 The intended reading is that $w$ is at least as close to the ideal represented by $A$ as $w'$ iff all the ideal propositions in $A$ which are true in $w'$ are also true in $w$.
+From this, Kratzer defines a the semantics for a list of different expressions, like `good possibility', `possibility' and so on.
+For our purposes, it suffices to look at those definitions involved in defining the meaning of \emph{probably $\alpha$}.
 
-From this, Kratzer defines a the semantics for a list of different expressions, like `good possibility', `possibility' and so on.
-For our purposes, it suffices to look at those definitions involved in defining the model `probable'.
-\begin{align*}
- \llbracket \varphi \succeq \psi \rrbracket^{f,g,w} &= \forall u \in (\medcap f(w) \cap q) \exists v \in \medcapf(w): v \leq_{g(w)}u ~\&~ v \in \llbracket \varphi \rrbracket 
-\end{align*}
+First, define `as least as good a possibility as'.
+The induced order on worlds $\leq_{g(w)}$ is `lifted' to an order on the level of propositions.
+For a modal base $f$ and a ordering source $g$, for propositions $p,q$ and world $w$, we can define
+\[
+    p \succeq_w q :\iff \forall b \in B_w \exists a \in A_w: a \succeq_{g(w)} b,
+\]
+where $A_w = \bigcap f(w) \cap A$, and $B_w$ analogously (cf. \cite[][p.~519]{holliday13_measur}).
+In words, a proposition $p$ is as least as good a possibility as a proposition $q$ seen from a world $w$ iff for any world in $q$ epistemically accessible from $w$ there is a world in $p$ accessible from $w$ that is at least as close to the ideal picked out $g(w)$.
+
+Next, `a better possibility': $p \succ_w q :\iff p \succeq_w q ~\&~ q \not\succeq_w p$.  
+Finally, we can assign a meaning to \emph{probably $\alpha$} given a set of worlds $W$, a modal base $f$ and a ordering source $g$ \parencite[][p.~645]{kratzer91_modal}:
+\[
+\llbracket \text{probably } \alpha \rrbracket^{f,g,w} = 1 :\iff \lb \alpha \rb \succ_w \lb \neg\alpha \rb
+\]
+Assuming here that we are looking at a flat fragment and $\alpha$ doesn't contain modals itself.
+Intuitively,... [briefly explain]
+\subsection{Discussion}
+
+The account presented has a couple of advantages.
+
+- Neatly fits with the other modals, just change f and g
+
+- Gives an account of probable without resorting to probability measures (give argument by Hamblin - maybe more in philosophy texts? check titelbaum)
+
+- solves problems describes in Kratzer text (probably dont reiterate)
+
+- more
+
+But it also suffers from crippling counterexamples, as will be explained in the next section.
 
@@
 Introduce the adequacy conditions V1-VXX etc.
+
+In his \parencite*{yalcin10_probab_operat}, Yalcin critically evaluates Kratzer's relative likelihood account and also Hamblin's account, which is based on the notion of possiblity (resp.
+plausiblity) measures \parencite{hamblin59_modal_probab}.
+Yalcin does this by following the good philosophical practice of establishing a set of desiderata the accounts can be evaluated against.
+In the case for judging semantics for a natural language phenomenon, these naturally come in the form of inference patterns that strike one as intuitively valid or invalid.
+The practice is fruitful because it gives criteria to compare different accounts in a transparent and comprehensible fashion, and shifts the focus of the problematic notion of \emph{intuitive plausibility} from judging the accounts themselves to judging the plausibility of the inference patterns.
+Whether some formally specified semantics validates a given inference pattern is then simply not a matter of debate and can be shown mathematically given the assumptions one is forced to make explicit.
+\begin{center}
+    \begin{prooftree}
+        \hypo{ \triangle \varphi } \infer1[(V1)]{ \neg \triangle \neg \varphi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+        \hypo{ \triangle (\varphi \land \psi)} \infer1[(V2)]{ \triangle \varphi \land \triangle \psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+        \hypo{ \triangle \varphi} \infer1[(V3)]{ \triangle (\varphi \lor \triangle \psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ } \infer1[(V4)]{ \varphi \succeq \bot}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ } \infer1[(V5)]{ \top \succeq \varphi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \Box \varphi } \infer1[(V6)]{ \triangle \varphi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \triangle \varphi } \infer1[(V7)]{ \Diamond \varphi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \psi \succeq \varphi } \hypo{\triangle \varphi} \infer2[(V11)]{ \triangle \psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \psi \succeq \varphi } \hypo{\triangle \varphi} \infer2[(V8)]{ \triangle \psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \psi \succeq \varphi } \hypo{\varphi \succeq \neg\varphi}\infer2[(V12)]{ \psi \succeq \neg\psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \varphi \succeq \psi } \hypo{\varphi \succeq \chi}\infer2[(I1)]{ \varphi \succeq (\psi \lor \chd)}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \varphi \succeq \neg \varphi } \infer1[(I2)]{ \varphi \succeq \psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \triangle \varphi } \infer1[(I3)]{ \varphi \succeq \psi}
+    \end{prooftree}
+\end{center}
+
 \section{Holliday and Icard's Generalisation to Measure Semantics}

### 2019-03-22 paper.tex
added adequacy conditions

@@
 \usepackage{multicol}
+\usepackage{calrsfs}
 
@@
 \addbibresource{/home/gilbert/Documents/bibliography/references.bib}
+\theoremstyle{definition}
+
+\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}
+
+\newtheorem{definition}{Definition}
 
 \newcommand*{\medcap}{\mathbin{\scalebox{1.5}{\ensuremath{\cap}}}}%
-\renewcommand{\L}{\mathcal{L}}
+\renewcommand{\L}{\pazocal{L}}
+\renewcommand{\F}{\pazocal{F}}
 \newcommand{\lb}{\llbracket}
 \newcommand{\rb}{\rrbracket}
+
 \begin{document}
@@
 The \emph{modal base} determines for every world the set of worlds which are epistemically accessible from it.
-More formally, the modal base is a function $f: W \rightarrow \wp(P)$ assigning each world $w$ a set of propositions.
-The set of propositions $f(w)$ assigned to $w$ represents, in the epistemic case, what we know at $w$.
-The set of epistemically accessible worlds then is $\bigcap f(w)$.
+More formally, the modal base is a function $f: W \rightarrow \wp(W)$ assigning each world $w$ a set of worlds.
+The set of worlds $f(w)$ assigned to $w$ represents, in the epistemic case, what we know at $w$.
 
-The \emph{ordering source} is a function $g: W \rightarrow \wp(P)$ s.t.
+The \emph{ordering source} is a function $g: W \rightarrow \wp(W)$ s.t.
 each $w$ is assigned a set of propositions $g(w)$ which interpreted as an \emph{ideal} (cf.
@@
 The ordering source induces a partial order (reflexive, antisymmetric and transitive) $\leq_{g(w)}$ as follows for all $w,w' \in W$:
-\[
+\begin{equation}
+    \label{eq:porder}
 w \leq_{g(w)} w' :\iff \{p: p\in g(w) ~\&~ w' \in p\} \subseteq \{p: p\in  g(w) ~\&~ w \in p\}
-\]
-The intended reading is that $w$ is at least as close to the ideal represented by $A$ as $w'$ iff all the ideal propositions in $A$ which are true in $w'$ are also true in $w$.
+\end{equation}
+The intended reading is that $w$ is at least as close to the ideal represented by $g(w)$ as $w'$ iff all the ideal propositions in $g(w)$ which are true in $w'$ are also true in $w$.
 From this, Kratzer defines a the semantics for a list of different expressions, like `good possibility', `possibility' and so on.
@@
 For a modal base $f$ and a ordering source $g$, for propositions $p,q$ and world $w$, we can define
-\[
-    p \succeq_w q :\iff \forall b \in B_w \exists a \in A_w: a \succeq_{g(w)} b,
-\]
-where $A_w = \bigcap f(w) \cap A$, and $B_w$ analogously (cf. \cite[][p.~519]{holliday13_measur}).
+\begin{equation}
+    \label{eq:lifted}
+    p \succeq_w q :\iff \forall b \in B_w \exists a \in A_w: a \leq_{g(w)} b,
+\end{equation}
+where $A_w = f(w) \cap A$, and $B_w$ analogously (cf. \cite[][p.~519]{holliday13_measur}).
 In words, a proposition $p$ is as least as good a possibility as a proposition $q$ seen from a world $w$ iff for any world in $q$ epistemically accessible from $w$ there is a world in $p$ accessible from $w$ that is at least as close to the ideal picked out $g(w)$.
@@
 Finally, we can assign a meaning to \emph{probably $\alpha$} given a set of worlds $W$, a modal base $f$ and a ordering source $g$ \parencite[][p.~645]{kratzer91_modal}:
-\[
+\begin{equation}
 \llbracket \text{probably } \alpha \rrbracket^{f,g,w} = 1 :\iff \lb \alpha \rb \succ_w \lb \neg\alpha \rb
-\]
+\end{equation}
 Assuming here that we are looking at a flat fragment and $\alpha$ doesn't contain modals itself.
 Intuitively,... [briefly explain]
+
+\begin{definition}
+    A \emph{Kratzer-style preferential model} is a tuple $M = \langle W,f,g,V \rangle$ s.t.
+    \begin{itemize}[nosep]
+\renewcommand\labelitemi{--}
+      \item $W$ is a non-empty set of possible worlds,
+      \item $f,g$ are functions $f,g: W \rightarrow \wp(W)$,
+      \item $V$ is a function $V: \text{Atom} \rightarrow \wp(W)$
+    \end{itemize}
+\end{definition}
+
+Further, we want the induced order defined above also hold for $M$.
+This is done in the following uninteresting definition: Let $f$ be a modal base, $g$ be a ordering source, $W$ a set of worlds.
+For each $w \in W$ let $\succeq_w$ be the order on subsets of $W$ defined in Equation \ref{eq:lifted}.
+Let $M = \langle W,f,g,V \rangle$ be a Kratzer-style preferential model.
+For $p,q \subseteq W$ we define an induced order on $\wp(W)$:
+\begin{equation}
+    \label{eq:induced}
+       p \succeq^{M,w} q \text{ iff } p \succeq_w q.
+\end{equation}
+
+\begin{definition}[Kratzer-style semantics]
+    \label{def:kratsem}
+    Let $M = \langle M,f,g,V \rangle$ be a Kratzer-style preferential model, $w \in W$, $\varphi, \psi \in \L$ and let $\succeq^{M,w}$ be the induced order on $\wp(W)$ by Equation \ref{eq:induced}.
+We define
+
+    \begin{enumerate}[nosep]
+        \renewcommand\labelitemi{--}
+      \item If $p \in \text{Atom}$, $M,w \models p$ iff $w \in V(p)$,
+      \item $M,w \models (\varphi \land \psi)$ iff $M,w \models \varphi$ and $M,w \models \psi$,
+      \item $\lb \varphi \rb = \{w' \in W : M,w' \models \varphi\}$,
+      \item $M,w \models \varphi \succeq \psi$ iff $\lb \varphi \rb^M \succeq^{M,w} \lb \psi \rb^M$,
+      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succeq^{M,w} \neg \varphi$,
+      \item $M,w \models \Diamond \varphi$ iff ...
+    \end{itemize}
+\end{definition}
+
 \subsection{Discussion}
@@
 Introduce the adequacy conditions V1-VXX etc.
+
+% \noindent A $\sigma$-algebra $\F$ on $W$ is a subset of $\wp(W)$ satisfying
+% \begin{enumerate}[nosep]
+%   \item $W \in \F$,
+%   \item $A \in \F \Rightarrow \bar{A} \in \F$, and
+%   \item $A_i \in \F \Rightarrow \bigcup^\infty A_i \in \F$
+% \end{enumerate}
+% For $A \subseteq W, i \in \mathbb{N}$. Let $\mathfrak{F^W}$ be the set of sigma algebras on subsets of $W$.
+
+% \noindent A probability function $P $
+
+\begin{definition}
+    A Yalcin-style probability model is a tuple $M = \langle W,R,V,\mathcal{F},\Pr\rangle$ such that
+    \begin{itemize}[nosep]
+        \renewcommand\labelitemi{--}
+      \item $W$ is a \mathbb{finite} set of possible worlds,
+      \item $R$ is a binary relation on $W$,
+        \item $V$ is a function $V: \text{Atom} \rightarrow \wp(W)$,
+        \item $\mathcal{F}$ is a function assigning each world $w \in W$ a boolean algebra $\F_w$ on $R(w)$, and 
+          \item $\Pr$ is a function assigning each world $w \in W$ a probability function \\ $p_w: \F_w \rightarrow [0,1]$.
+    \end{itemize}
+\end{definition}
+
+\begin{definition}[Yalcin-style semantics]
+    \label{def:yalcsem}
+    Let $M = \langle M,R,V,\mathcal{F},\Pr \rangle$ be a Yalcin-style probability model, $w \in W$, $\varphi, \psi \in \L$.
+We define clauses 1-3 just like in Kratzer-style preferential models (Definition \ref{def:kratsem}).
+We define further:
+    \begin{enumerate}[nosep]
+  \setcounter{enumi}{3}
+      \item $M,w \models \varphi \succeq \psi$ iff $p_w(\lb \varphi \rb^M) \geq p_w(\lb \psi \rb^M) $
+      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ^{M,w} \neg \varphi$ iff $ p_w(\lb \varphi \rb^M) > .5$
+    \end{enumerate}
+\end{definition}
 
@@
 \begin{prooftree}
-    \hypo{ \varphi \succeq \psi } \hypo{\varphi \succeq \chi}\infer2[(I1)]{ \varphi \succeq (\psi \lor \chd)}
+    \hypo{ \varphi \succeq \psi } \hypo{\varphi \succeq \chi}\infer2[(I1)]{ \varphi \succeq (\psi \lor \chi)}
     \end{prooftree}

### 2019-03-23 paper.tex
Added more precise semantics

@@
 \newcommand{\rb}{\rrbracket}
+\newcommand{\Po}{\text{Po}}
 
+\newcommand{\succeqK}{\succeq^K_{M,w}}
 \begin{document}
@@
 \onehalfspacing
+
 \maketitle
 
+\tableofcontents
 \section{Introduction}
@@
 \section{The Epistemic Modal \emph{probable}}
+Give some natural language motivation
+
 Also show the need for expanding the standard intensional semantics!
+
 How is probable to be evaluated? MacFarlane's Solipcism.
 
-To base the following discussions on a common language, we follow the definitions of a propositional language $\L$ by \textcite{harrison-trainor17_prefer} and \textcite{holliday13_measur}:
+To base the following discussions on a common language, we define a
+propositional language $\L$ like \textcite{harrison-trainor17_prefer} and
+\textcite{holliday13_measur} do:
 \[
-\varphi ::= p ~|~ \neg \varphi ~|~ (\varphi \land \psi) ~|~ (\varphi \rightarrow \psi) ~|~ (\varphi \vee \psi) ~|~ (\varphi \succeq \psi) ~|~ \triangle\varphi 
+\varphi ::= p ~|~ \neg \varphi ~|~ (\varphi \land \psi) ~|~  (\varphi \succeq \psi) ~|~ \triangle\varphi 
 \]
-The intended readings for the Boolean operators are completely standard.
+The other boolean connectives $(\varphi \rightarrow \psi), (\varphi \vee
+\psi)$ are defined in the standard way from negation and conjunction. The
+intended readings for the Boolean operators are also standard, we add the following:
 \begin{align*}
@@
 
-\section{Kratzer's Analysis}
+\section{Kratzer's Preferential Semantics}
 
@@
 \end{enumerate}
-Here, the modalities are listed in decreasing strength, such that the intended reading is that a) implies b), b) implies c), and so forth.
+Here, the modalities are listed in decreasing strength, such that the intended
+reading is that a) implies b), b) implies c), and so forth.
 Note that is a qualitative approach to graded modals, as opposed to quantitative approaches, employing a scale structure in the semantics.
-\textcite{yalcin10_probab_operat} calls it a `relative likelihood' approach.
 
-\subsection{Kratzer's Formal Setup}
 How do the semantics look like?
@@
 
+\subsection{Formal Setup}
+
+To put it slightly more formally, we define: 
 \begin{definition}
-    A \emph{Kratzer-style preferential model} is a tuple $M = \langle W,f,g,V \rangle$ s.t.
+    A \emph{Kratzer preferential model} is a tuple $M = \langle W,f,g,V \rangle$ s.t.
     \begin{itemize}[nosep]
@@
 Further, we want the induced order defined above also hold for $M$.
-This is done in the following uninteresting definition: Let $f$ be a modal base, $g$ be a ordering source, $W$ a set of worlds.
-For each $w \in W$ let $\succeq_w$ be the order on subsets of $W$ defined in Equation \ref{eq:lifted}.
-Let $M = \langle W,f,g,V \rangle$ be a Kratzer-style preferential model.
+This is done in the following uninteresting definition:
+Let $f$ be a modal base, $g$ be a ordering source, $W$ a set of worlds.
+For each $w \in W$ let $\succeq_w$ be the order on subsets of $W$ defined in
+Equation \ref{eq:lifted}.
+Let $M = \langle W,f,g,V \rangle$ be a Kratzer preferential model.
 For $p,q \subseteq W$ we define an induced order on $\wp(W)$:   
@@
 
-\begin{definition}[Kratzer-style semantics]
+\begin{definition}[Kratzer preferential semantics]
     \label{def:kratsem}
-    Let $M = \langle M,f,g,V \rangle$ be a Kratzer-style preferential model, $w \in W$, $\varphi, \psi \in \L$ and let $\succeq^{M,w}$ be the induced order on $\wp(W)$ by Equation \ref{eq:induced}.
+    Let $M = \langle M,f,g,V \rangle$ be a Kratzer preferential model, $w \in W$, $\varphi, \psi \in \L$ and let $\succeq^{M,w}$ be the induced order on $\wp(W)$ by Equation \ref{eq:induced}.
 We define
@@
       \item If $p \in \text{Atom}$, $M,w \models p$ iff $w \in V(p)$,
+      \item $M,w \models \neg \varphi$ iff $M,w \not\models \varphi$
       \item $M,w \models (\varphi \land \psi)$ iff $M,w \models \varphi$ and $M,w \models \psi$,
-      \item $\lb \varphi \rb = \{w' \in W : M,w' \models \varphi\}$,
+      \item $\lb \varphi \rb^M = \{w' \in W : M,w' \models \varphi\}$,
       \item $M,w \models \varphi \succeq \psi$ iff $\lb \varphi \rb^M \succeq^{M,w} \lb \psi \rb^M$,
-      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succeq^{M,w} \neg \varphi$,
+      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succeq \neg \varphi$,
       \item $M,w \models \Diamond \varphi$ iff ...
@@
 
-But it also suffers from crippling counterexamples, as will be explained in the next section.
+But it also suffers from crippling counterexamples:
 
-\section{Yalcin and Lassiter's Probability Semantics}
-Introduce the adequacy conditions V1-VXX etc.
+\section{Hamblin's Possibility Semantics}
+
+\noindent A possibility function is a function $p: \F \rightarrow [0,1]$ such that
+\begin{enumerate}[nosep]
+  \item $p(\emptyset) = 0$ 
+  \item $p(W) = 1$
+  \item $p(U \cup V) = \max(p(U),p(V))$
+\end{enumerate}
+\noindent A boolean algebra on $W$ is a set $\F \subseteq \wp(W)$ such that
+\begin{enumerate}[nosep]
+  \item $\emptyset, W \in \F$,
+  \item $A \in \F \Rightarrow \bar{A} \in \F$
+  \item $A,B \in \F \Rightarrow A \cup B \in \F$
+\end{enumerate}
+
+Following \textcite{hamblin59_modal_probab},
+\textcite[][pp.~42]{halpern03_reason_about_uncer} and Yalcin's
+\parencite*{yalcin10_probab_operat} reinterpretation to fit Hamblin's account into modern
+semantics, we define the following: 
+\begin{definition}
+    A \emph{Hamblin possibility model} is a tuple $M = \langle W,R,V,\mathcal{F},\Po\rangle$ such that
+    \begin{itemize}[nosep]
+        \renewcommand\labelitemi{--}
+      \item $W$ is a \mathbb{finite} set of possible worlds,
+      \item $R$ is a binary relation on $W$,
+        \item $V$ is a function $V: \text{Atom} \rightarrow \wp(W)$,
+        \item $\mathcal{F}$ is a function assigning each world $w \in W$ a boolean algebra $\F_w$ on $R(w)$, and 
+          \item $\Po$ is a function assigning each world $w \in W$ a possibility function \\ $p_w: \F_w \rightarrow [0,1]$.
+    \end{itemize}
+\end{definition}
+
+\begin{definition}[Hamblin possiblity semantics]
+    \label{def:hambsem}
+    Let $M = \langle M,R,V,\mathcal{F},\Pr \rangle$ be a Hamblin possiblity model, $w \in W$, $\varphi, \psi \in \L$.
+We define clauses 1-4 just like in Kratzer preferential semantics (Definition \ref{def:kratsem}).
+We define further:
+    \begin{enumerate}[nosep]
+  \setcounter{enumi}{5}
+      \item $M,w \models \varphi \succeq \psi$ iff $p_w(\lb \varphi \rb^M) \geq p_w(\lb \psi \rb^M) $
+      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ \neg \varphi$ 
+    \end{enumerate}
+\end{definition}
+
+\section{Yalcin's Probability Semantics}
 
@@
 \begin{definition}
-    A Yalcin-style probability model is a tuple $M = \langle W,R,V,\mathcal{F},\Pr\rangle$ such that
+    A Yalcin probability model is a tuple $M = \langle W,R,V,\mathcal{F},\Pr\rangle$ such that
     \begin{itemize}[nosep]
@@
         \item $\mathcal{F}$ is a function assigning each world $w \in W$ a boolean algebra $\F_w$ on $R(w)$, and 
-          \item $\Pr$ is a function assigning each world $w \in W$ a probability function \\ $p_w: \F_w \rightarrow [0,1]$.
+          \item $\Pr$ is a function assigning each world $w \in W$ a probability function \\ $\mu_w: \F_w \rightarrow [0,1]$.
     \end{itemize}
@@
 
-\begin{definition}[Yalcin-style semantics]
+\begin{definition}[Yalcin probability semantics]
     \label{def:yalcsem}
-    Let $M = \langle M,R,V,\mathcal{F},\Pr \rangle$ be a Yalcin-style probability model, $w \in W$, $\varphi, \psi \in \L$.
-We define clauses 1-3 just like in Kratzer-style preferential models (Definition \ref{def:kratsem}).
+    Let $M = \langle M,R,V,\mathcal{F},\Pr \rangle$ be a Yalcin probability model, $w \in W$, $\varphi, \psi \in \L$.
+We define clauses 1-3 just like in Kratzer preferential models (Definition \ref{def:kratsem}).
 We define further:
     \begin{enumerate}[nosep]
-  \setcounter{enumi}{3}
-      \item $M,w \models \varphi \succeq \psi$ iff $p_w(\lb \varphi \rb^M) \geq p_w(\lb \psi \rb^M) $
-      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ^{M,w} \neg \varphi$ iff $ p_w(\lb \varphi \rb^M) > .5$
+  \setcounter{enumi}{4}
+      \item $M,w \models \varphi \succeq \psi$ iff $\mu_w(\lb \varphi \rb^M) \geq \mu_w(\lb \psi \rb^M) $
+      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ^{M,w} \neg \varphi$ iff $ \mu_w(\lb \varphi \rb^M) > .5$
     \end{enumerate}
@@
 
-\section{Holliday and Icard's Generalisation to Measure Semantics}
-\section{Holliday and Icard's Unification of Preferential and Probabilistic Semantics}
+\section{Holliday and Icard's Preferential Semantics}
+
 \section{Conclusion}

### 2019-03-23 paper.tex
added substantial structure to the paper

@@
 We might leave uninterpreted some elements which don't figure prominently in the respective theory discussed at that moment.
+
+In his \parencite*{yalcin10_probab_operat}, Yalcin critically evaluates Kratzer's relative likelihood account and also Hamblin's account, which is based on the notion of possiblity (resp.
+plausiblity) measures \parencite{hamblin59_modal_probab}.
+Yalcin does this by following the good philosophical practice of establishing a set of desiderata the accounts can be evaluated against.
+In the case for judging semantics for a natural language phenomenon, these naturally come in the form of inference patterns that strike one as intuitively valid or invalid.
+The practice is fruitful because it gives criteria to compare different accounts in a transparent and comprehensible fashion, and shifts the focus of the problematic notion of \emph{intuitive plausibility} from judging the accounts themselves to judging the plausibility of the inference patterns.
+Whether some formally specified semantics validates a given inference pattern is then simply not a matter of debate and can be shown mathematically given the assumptions one is forced to make explicit.
+\begin{center}
+    \begin{prooftree}
+        \hypo{ \triangle \varphi } \infer1[(V1)]{ \neg \triangle \neg \varphi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+        \hypo{ \triangle (\varphi \land \psi)} \infer1[(V2)]{ \triangle \varphi \land \triangle \psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+        \hypo{ \triangle \varphi} \infer1[(V3)]{ \triangle (\varphi \lor \psi)}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ } \infer1[(V4)]{ \varphi \succeq \bot}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ } \infer1[(V5)]{ \top \succeq \varphi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \Box \varphi } \infer1[(V6)]{ \triangle \varphi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \triangle \varphi } \infer1[(V7)]{ \Diamond \varphi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \psi \succeq \varphi } \hypo{\triangle \varphi} \infer2[(V11)]{ \triangle \psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \psi \succeq \varphi } \hypo{\varphi \succeq \neg\varphi}\infer2[(V12)]{ \psi \succeq \neg\psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \varphi \succeq \psi } \hypo{\varphi \succeq \chi}\infer2[(I1)]{ \varphi \succeq (\psi \lor \chi)}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \varphi \succeq \neg \varphi } \infer1[(I2)]{ \varphi \succeq \psi}
+    \end{prooftree}
+\end{center}
+
+\begin{center}
+\begin{prooftree}
+    \hypo{ \triangle \varphi } \infer1[(I3)]{ \varphi \succeq \psi}
+    \end{prooftree}
+\end{center}
 
@@
 \section{Hamblin's Possibility Semantics}
-
+\subsection{Formal Setup}
 \noindent A possibility function is a function $p: \F \rightarrow [0,1]$ such that
@@
 \end{definition}
-
+\subsection{Discussion}
 \section{Yalcin's Probability Semantics}
@@
 % \noindent A probability function $P $
-
+\subsection{Formal Setup}
 \begin{definition}
@@
 
-In his \parencite*{yalcin10_probab_operat}, Yalcin critically evaluates Kratzer's relative likelihood account and also Hamblin's account, which is based on the notion of possiblity (resp.
-plausiblity) measures \parencite{hamblin59_modal_probab}.
-Yalcin does this by following the good philosophical practice of establishing a set of desiderata the accounts can be evaluated against.
-In the case for judging semantics for a natural language phenomenon, these naturally come in the form of inference patterns that strike one as intuitively valid or invalid.
-The practice is fruitful because it gives criteria to compare different accounts in a transparent and comprehensible fashion, and shifts the focus of the problematic notion of \emph{intuitive plausibility} from judging the accounts themselves to judging the plausibility of the inference patterns.
-Whether some formally specified semantics validates a given inference pattern is then simply not a matter of debate and can be shown mathematically given the assumptions one is forced to make explicit.
-\begin{center}
-    \begin{prooftree}
-        \hypo{ \triangle \varphi } \infer1[(V1)]{ \neg \triangle \neg \varphi}
-    \end{prooftree}
-\end{center}
+\subsection{Discussion}
+\section{Holliday and Icard's Preferential Semantics}
+\subsection{Formal Setup}
+\begin{definition}
+    A Holliday and Icard preferential model is a tuple $M = {\langle
+      W,R,V,\succeq\rangle}$ such that
+    \begin{itemize}[nosep]
+        \renewcommand\labelitemi{--}
+      \item $W$ is a set of possible worlds,
+      \item $R$ is a binary relation on $W$,
+      \item $V$ is a function $V: \text{ Atom } \rightarrow \wp(W)$, and
+      \item $\succeq$ is a function assigning each world $w \in W$ a preorder
+        (reflexive and transitive binary relation) $\geq^{M,w}$ on $W$. 
+    \end{itemize}
+\end{definition}
+Further, for two proposition $A,B \subseteq W$ we define
+\begin{multline}
+    \label{eq:injection}A \succeq^{M,w} B :\iff \text{ there exists an injective function } f: B \rightarrow A \\ \text{ such that } f(x) \geq^{M,w} x \text{ for all } x \in B.
+\end{multline}
 
-\begin{center}
-\begin{prooftree}
-        \hypo{ \triangle (\varphi \land \psi)} \infer1[(V2)]{ \triangle \varphi \land \triangle \psi}
-    \end{prooftree}
-\end{center}
+\begin{definition}[Holliday and Icard preferential semantics] Let $M = {\langle
+      W,R,V,\succeq \rangle}$, $w \in W, \varphi,\psi \in \L$ and let $\succeq^{M,w}$ be the order on $W$ defined by Equation \ref{eq:injection}.
+We the define clauses 1-6 just like in Kratzer preferential semantics (Definition \ref{def:kratsem}).
+\end{definition}
 
-\begin{center}
-\begin{prooftree}
-        \hypo{ \triangle \varphi} \infer1[(V3)]{ \triangle (\varphi \lor \triangle \psi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ } \infer1[(V4)]{ \varphi \succeq \bot}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ } \infer1[(V5)]{ \top \succeq \varphi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \Box \varphi } \infer1[(V6)]{ \triangle \varphi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \triangle \varphi } \infer1[(V7)]{ \Diamond \varphi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \psi \succeq \varphi } \hypo{\triangle \varphi} \infer2[(V11)]{ \triangle \psi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \psi \succeq \varphi } \hypo{\triangle \varphi} \infer2[(V8)]{ \triangle \psi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \psi \succeq \varphi } \hypo{\varphi \succeq \neg\varphi}\infer2[(V12)]{ \psi \succeq \neg\psi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \varphi \succeq \psi } \hypo{\varphi \succeq \chi}\infer2[(I1)]{ \varphi \succeq (\psi \lor \chi)}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \varphi \succeq \neg \varphi } \infer1[(I2)]{ \varphi \succeq \psi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \triangle \varphi } \infer1[(I3)]{ \varphi \succeq \psi}
-    \end{prooftree}
-\end{center}
-
-\section{Holliday and Icard's Preferential Semantics}
-
+\subsection{Discussion}
 \section{Conclusion}

### 2019-03-23 paper.tex
added substantial structure to the paper

@@
 \title{The Epistemic Modal \emph{probable}: Qualitative and Quantitative Accounts}
-\author{Conrad Friedrich \\ MCMP, LMU Munich \\ 1,337 words}
+\author{Conrad Friedrich \\ MCMP, LMU Munich }
 \date{\today}
@@
 \usepackage{setspace}
-% Used to scale \medcap
-\usepackage{graphicx}
+
 \usepackage{ebproof/ebproof}
-\usepackage{multicol}
 \usepackage{calrsfs}
+% Used for todo notes
+\usepackage{xcolor}
 
@@
 
-\newcommand*{\medcap}{\mathbin{\scalebox{1.5}{\ensuremath{\cap}}}}%
+\newcommand\todo[1]{\textcolor{red}{#1}}
+
 \renewcommand{\L}{\pazocal{L}}
-\renewcommand{\F}{\pazocal{F}}
+\newcommand{\F}{\pazocal{F}}
 \newcommand{\lb}{\llbracket}
@@
 
+\todo{
+  \begin{itemize}[nosep]
+    \item Write an Introduction
+  \end{itemize}
+}
 \section{Intensional Semantics}
+\todo{ \begin{itemize}[nosep]
+  \item Tie the paper into framework used in class
+\end{itemize} }
+
 Note that we don't need first order logic. 
@@
 \section{The Epistemic Modal \emph{probable}}
-Give some natural language motivation
-
-Also show the need for expanding the standard intensional semantics!
-
-How is probable to be evaluated? MacFarlane's Solipcism.
+\todo{\begin{itemize}[nosep]
+    \item  Give some natural language motivation
+    \item Also show the need for expanding the standard intensional semantics!
+    \item How is probable to be evaluated? MacFarlane's Solipcism.
+  \end{itemize}
+}
 
@@
 \[
-\varphi ::= p ~|~ \neg \varphi ~|~ (\varphi \land \psi) ~|~  (\varphi \succeq \psi) ~|~ \triangle\varphi 
+\varphi ::= p ~|~ \neg \varphi ~|~ (\varphi \land \psi) ~|~  (\varphi \succeq \psi) ~|~ \triangle\varphi ~|~ \Diamond \varphi
 \]
 The other boolean connectives $(\varphi \rightarrow \psi), (\varphi \vee
-\psi)$ are defined in the standard way from negation and conjunction. The
-intended readings for the Boolean operators are also standard, we add the following:
+\psi)$ as well as $\top, \bot$ are defined in the standard way from negation and conjunction.
+Define further $\Box \varphi = \neg\Diamond\neg \varphi$.
+The intended readings are as follows:
 \begin{align*}
-  \varphi \succeq \psi &: \varphi \text{ is at least as likely as } \psi \\
-  \triangle \varphi &:\text{probably } \varphi.
+  \varphi \succeq \psi &: \varphi \text{ is at least as likely as } \psi. \\
+  \triangle \varphi &:\text{probably } \varphi. \\ 
+                      \Diamond \varphi &: \text{It might be that } \varphi.
 \end{align*}
-We might leave uninterpreted some elements which don't figure prominently in the respective theory discussed at that moment.
 
+\subsection{Criteria for Adequacy}
 In his \parencite*{yalcin10_probab_operat}, Yalcin critically evaluates Kratzer's relative likelihood account and also Hamblin's account, which is based on the notion of possiblity (resp.
@@
 Whether some formally specified semantics validates a given inference pattern is then simply not a matter of debate and can be shown mathematically given the assumptions one is forced to make explicit.
+\todo{
+\begin{itemize}[nosep]
+  \item Motivate and describe the conditions
+\end{itemize}
+}
 \begin{center}
@@
 
+Yalcin and also \textcite{lassiter10_gradab} introduce an additional criterion
+\todo{
+  \begin{itemize}
+    \item Discuss additional criterion, NEGATIVBESCHEID
+  \end{itemize}
+}
 \section{Kratzer's Preferential Semantics}
-
+\todo{
+  \begin{itemize}
+    \item Clean up this section a bit
+  \end{itemize}
+}
 For \textcite{kratzer91_modal} epistemic modals like \emph{probably} are just a special case of a more general class of modal auxiliaries.
@@
 
+\todo{\begin{itemize}[nosep]
+  \item The account presented has a couple of advantages.
+\item Neatly fits with the other modals, just change f and g
+\item Gives an account of probable without resorting to probability measures (give argument by Hamblin - maybe more in philosophy texts? check titelbaum)
+\item solves problems describes in Kratzer text (probably dont reiterate)  
+\end{itemize}
+}
 How do the semantics look like?
@@
 \cite{lewis81_order_seman_premis_seman_count}).
-The ordering source induces a partial order (reflexive, antisymmetric and transitive) $\leq_{g(w)}$ as follows for all $w,w' \in W$:
+The ordering source induces an order $\leq_{g(w)}$ on $W$ for all $w,w' \in W$ as follows:
 \begin{equation}
@@
 w \leq_{g(w)} w' :\iff \{p: p\in g(w) ~\&~ w' \in p\} \subseteq \{p: p\in  g(w) ~\&~ w \in p\}
+\end{equation}
+\todo{THIS NEED UPDATING SINCE g(w) CHANGED!}
+\begin{equation}
+    \label{eq:porder}
+w \leq_{g(w)} w' :\iff \{A: g(w) \subseteq A ~\&~ w' \in A\} \subseteq \{A: g(w) \subseteq A ~\&~ w \in A\}
 \end{equation}
@@
 The induced order on worlds $\leq_{g(w)}$ is `lifted' to an order on the level of propositions.
-For a modal base $f$ and a ordering source $g$, for propositions $p,q$ and world $w$, we can define
+For a modal base $f$ and a ordering source $g$, for propositions $A,B$ and world $w$, we can define
 \begin{equation}
     \label{eq:lifted}
-    p \succeq_w q :\iff \forall b \in B_w \exists a \in A_w: a \leq_{g(w)} b,
+    A \succeq_w B :\iff \forall b \in B_w \exists a \in A_w: a \leq_{g(w)} b,
 \end{equation}
 where $A_w = f(w) \cap A$, and $B_w$ analogously (cf. \cite[][p.~519]{holliday13_measur}).
-In words, a proposition $p$ is as least as good a possibility as a proposition $q$ seen from a world $w$ iff for any world in $q$ epistemically accessible from $w$ there is a world in $p$ accessible from $w$ that is at least as close to the ideal picked out $g(w)$.
+In words, a proposition $A$ is as least as good a possibility as a proposition $B$ seen from a world $w$ iff for any world in $B$ epistemically accessible from $w$ there is a world in $A$ accessible from $w$ that is at least as close to the ideal picked out by $g(w)$.
 
-Next, `a better possibility': $p \succ_w q :\iff p \succeq_w q ~\&~ q \not\succeq_w p$.  
+The strict part is defined as one would expect:
+
+\noindent $A \succ_w B :\iff {A \succeq_w B ~\&~ B \not\succeq_w A}$.
+
 Finally, we can assign a meaning to \emph{probably $\alpha$} given a set of worlds $W$, a modal base $f$ and a ordering source $g$ \parencite[][p.~645]{kratzer91_modal}:
@@
     \begin{enumerate}[nosep]
-        \renewcommand\labelitemi{--}
       \item If $p \in \text{Atom}$, $M,w \models p$ iff $w \in V(p)$,
@@
       \item $M,w \models \varphi \succeq \psi$ iff $\lb \varphi \rb^M \succeq^{M,w} \lb \psi \rb^M$,
-      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succeq \neg \varphi$,
+      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succeq \neg \varphi ~\&~ \neg (\neg \varphi \succeq \varphi)$,
       \item $M,w \models \Diamond \varphi$ iff ...
-    \end{itemize}
+    \end{enumerate}
 \end{definition}
@@
 
-The account presented has a couple of advantages.
+How does Kratzer's account fare with respect to the adequacy conditions we defined?
+The semantics validate conditions (V1-V7), which can be easily seen by applying the definitions.
+For example, let us establish that Kratzer preferential semantics satisfy (V2), i.e.: 
+\begin{center}
+\begin{prooftree}
+        \hypo{ \triangle (\varphi \land \psi)} \infer1[(V2)]{ \triangle \varphi \land \triangle \psi}
+    \end{prooftree}
+\end{center}
+Suppose $M,w \models \triangle (\varphi \land \psi)$.
+Then $\lb (\varphi \land \psi) \rb^M \succ^{M,w} \lb \neg(\varphi \land \psi)\rb^M$.
+Let $y \in \lb \neg \varphi \rb^M$.
+Then $y \in \lb \neg \varphi \lor \neg\psi \rb^M = \lb \neg(\varphi \land \psi)\rb^M$.
+By assumption, there is an $x \in \lb (\varphi \land \psi) \rb^M$ such that $x \leq_{g(w)} y$.
+But then $x \in \lb \varphi \rb^M$, too.
+Hence $\lb \varphi \rb^M \succ^{M,w} \lb \neg \varphi \rb^M$ and thus $M,w \models \triangle \varphi$.
+The case for $M,w \models \triangle \psi$ works analogously.
 
-- Neatly fits with the other modals, just change f and g
-
-- Gives an account of probable without resorting to probability measures (give argument by Hamblin - maybe more in philosophy texts? check titelbaum)
-
-- solves problems describes in Kratzer text (probably dont reiterate)
-
-- more
-
-But it also suffers from crippling counterexamples:
+Kratzer's account does \emph{not} validate (V11-V12).
+\textcite[pp.~935, note~8]{yalcin10_probab_operat} gives a countermodel.
+In addition, the account \emph{does} validate pattern (I1), as can easily be seen.
+This is already an unwelcome result.
+Additionally, (I1) together with (V5) entails (I2) \parencite[p.~922]{yalcin10_probab_operat}.
+That is, on this account, anything that is probable is a least as likely as any tautology.
+This is, of course, a ruinous result.
 
 \section{Hamblin's Possibility Semantics}
+\todo{
+  \begin{itemize}
+    \item Write an Introduction and Purpose compared to Kratzer
+  \end{itemize}}
 \subsection{Formal Setup}
-\noindent A possibility function is a function $p: \F \rightarrow [0,1]$ such that
-\begin{enumerate}[nosep]
-  \item $p(\emptyset) = 0$ 
-  \item $p(W) = 1$
-  \item $p(U \cup V) = \max(p(U),p(V))$
-\end{enumerate}
-\noindent A boolean algebra on $W$ is a set $\F \subseteq \wp(W)$ such that
+\noindent Let $W$ be a set. A boolean algebra on $W$ is a set $\F \subseteq \wp(W)$ such that
 \begin{enumerate}[nosep]
@@
 
+\noindent Let $\F$ be a boolean algebra. A possibility function is a function $p: \F \rightarrow [0,1]$ such that
+\begin{enumerate}[nosep]
+  \item $p(\emptyset) = 0$ 
+  \item $p(W) = 1$
+  \item $p(U \cup V) = \max(p(U),p(V))$
+\end{enumerate}
 Following \textcite{hamblin59_modal_probab},
@@
         \renewcommand\labelitemi{--}
-      \item $W$ is a \mathbb{finite} set of possible worlds,
+      \item $W$ is a set of possible worlds,
       \item $R$ is a binary relation on $W$,
@@
 \subsection{Discussion}
+\todo{
+  \begin{itemize}
+    \item Write Discussion
+  \end{itemize}
+}
 \section{Yalcin's Probability Semantics}
 
-% \noindent A $\sigma$-algebra $\F$ on $W$ is a subset of $\wp(W)$ satisfying
-% \begin{enumerate}[nosep]
-%   \item $W \in \F$,
-%   \item $A \in \F \Rightarrow \bar{A} \in \F$, and
-%   \item $A_i \in \F \Rightarrow \bigcup^\infty A_i \in \F$
-% \end{enumerate}
-% For $A \subseteq W, i \in \mathbb{N}$. Let $\mathfrak{F^W}$ be the set of sigma algebras on subsets of $W$.
+\todo{
+  \begin{itemize}
+    \item Write Introduction
+  \end{itemize}
+}
+\subsection{Formal Setup}
 
-% \noindent A probability function $P $
-\subsection{Formal Setup}
+\noindent Let $\F$ be a boolean algebra. A probability function is a function $\mu: \F \rightarrow [0,1]$ such that
+\begin{enumerate}[nosep]
+  \item $\mu(\emptyset) = 0$ 
+  \item $\mu(W) = 1$
+  \item $\mu(U \cup V) = \mu(U) + \mu(V) \text{ if } U \cup V = \emptyset $
+\end{enumerate}
+
 \begin{definition}
-    A Yalcin probability model is a tuple $M = \langle W,R,V,\mathcal{F},\Pr\rangle$ such that
+    A \emph{Yalcin probability model} is a tuple $M = \langle W,R,V,\mathcal{F},\Pr\rangle$ such that
     \begin{itemize}[nosep]
         \renewcommand\labelitemi{--}
-      \item $W$ is a \mathbb{finite} set of possible worlds,
+      \item $W$ is a set of possible worlds,
       \item $R$ is a binary relation on $W$,
@@
 \subsection{Discussion}
+\todo{
+  \begin{itemize}
+    \item Write Discussion
+  \end{itemize}
+}
 \section{Holliday and Icard's Preferential Semantics}
+\todo{
+  \begin{itemize}
+    \item Write Introduction
+  \end{itemize}
+}
 \subsection{Formal Setup}
@@
 \end{definition}
-Further, for two proposition $A,B \subseteq W$ we define
+Let $R[w] = \{w':wRw'\}$. For any proposition $P \subseteq W$, $P_w := P \cap R[w]$. Further, for two proposition $A,B \subseteq W$ we define
 \begin{multline}
-    \label{eq:injection}A \succeq^{M,w} B :\iff \text{ there exists an injective function } f: B \rightarrow A \\ \text{ such that } f(x) \geq^{M,w} x \text{ for all } x \in B.
+    \label{eq:injection}A \succeq^{M,w} B :\iff \text{ there exists an injective function } f: B_w \rightarrow A_w \\ \text{ such that } f(x) \geq^{M,w} x \text{ for all } x \in B_w.
 \end{multline}
@@
 
+Holliday and Icard's semantics is very similar to Kratzer's.
+In particular, we can associate the modal base and ordering source of Kratzer's with the binary relation $R$ and the $\geq$-function.
+Just as the modal base determines for each world a set of epistemically accessible worlds, so does $R[w]$.
+And just as the ordering source induces an order on propositions, so does $\geq$.
+For our present purposes, both formulations are equivalent even.
+Holliday and Icard make a crucial change to how the order is induced, however.
+To see this, note that Equation \ref{eq:lifted} can be rewritten as an equivalent definition:
+
+For a modal base $f$ and a ordering source $g$, for propositions $A,B$ and world $w$, define
+\begin{multline}
+    \tag{2*}
+    \label{eq:lifted-star}
+    A \succeq_w B :\iff \text{ there exists a function } f: B_w \rightarrow A_w \\ \text{ such that } f(x) \leq_{g(w)} x \text{ for all } x \in B_w.
+\end{multline}
+Compared to Equation \ref{eq:injection}, besides the inverted direction of $\geq$ which is just due to how the notions were defined, the difference is that Holliday and Icard require an injective function assigning each element of $B$ a unique element of $A$ such that the element of $A$ is more plausible, normal etc.
+This simple change has interesting consequences, as we will see in the next section.
 \subsection{Discussion}
+\todo{
+  \begin{itemize}
+    \item Write Discussion
+  \end{itemize}
+}
 \section{Conclusion}
+\todo{
+  \begin{itemize}
+    \item Write Conclusion and further studies
+  \end{itemize}
+}
 What about the $\epsilon$-semantics (Adams, Pearl)? 

### 2019-03-23 paper.tex
fleshed out middle sections

@@
 \documentclass{article}
-\title{The Epistemic Modal \emph{probable}: Qualitative and Quantitative Accounts}
+\title{The Epistemic Modal \emph{probable}}
 \author{Conrad Friedrich \\ MCMP, LMU Munich }
@@
     \item Write an Introduction
+     \item be perfectly clear as to what happens. SIGNPOST 
   \end{itemize}
@@
     \item Also show the need for expanding the standard intensional semantics!
-    \item How is probable to be evaluated? MacFarlane's Solipcism.
+    \item How is probable to be evaluated? Epistemic interpretation? MacFarlane's Solipcism.
+    \item Mention how Lassiter has a different, graded adjective based approach.
+    \item Discuss how absolute probability is best reduced to relative likelihood with the negation
+      \item note that there are a lot more interesting problems associated with probable but to have an readable paper need to focus on particulars.
   \end{itemize}
@@
 \]
-The other boolean connectives $(\varphi \rightarrow \psi), (\varphi \vee
+Where $p \in \text{Atom}$, i.e. an atomic formula. The other boolean connectives $(\varphi \rightarrow \psi), (\varphi \vee
 \psi)$ as well as $\top, \bot$ are defined in the standard way from negation and conjunction.
@@
 In his \parencite*{yalcin10_probab_operat}, Yalcin critically evaluates Kratzer's relative likelihood account and also Hamblin's account, which is based on the notion of possiblity (resp.
-plausiblity) measures \parencite{hamblin59_modal_probab}.
+plausiblity) functions \parencite{hamblin59_modal_probab}.
 Yalcin does this by following the good philosophical practice of establishing a set of desiderata the accounts can be evaluated against.
@@
 
-Yalcin and also \textcite{lassiter10_gradab} introduce an additional criterion
-\todo{
-  \begin{itemize}
-    \item Discuss additional criterion, NEGATIVBESCHEID
-  \end{itemize}
-}
+\subsection{Criteria not Considered}
+Yalcin and also \textcite{lassiter10_gradab} introduce an additional criterion motivated by examples of the following sort:
+\begin{enumerate}[nosep]
+  \item There is a 60\% probability that it is raining.
+  \item $\varphi$ is twice as likely as $\psi$.
+\end{enumerate}
+Yalcin argues that sentences of this type are ``used and interpreted by speakers who are innocent of the mathematical theory of probability'' \parencite[][p.~923]{yalcin10_probab_operat} and that a semantics for probability operators in natural language must be able to account for them, while Lassiter merely states it as a problem for preferential semantics \parencite[][p.~210]{lassiter10_gradab}.
+Both share the implicit assumption that both the qualitative talk (`probably $\varphi$') and the quantitative talk like in (2) above need to be accounted for by the same semantics.
+Given the methodological practice of frequent appeal to intuition to support claims of this sort, the assumption can also be doubted on the same grounds.
+It is equally plausible that people usually employ different notions of \emph{probable} (or \emph{likely}) in the qualitative and the quantitative case.
+Qualitative talk is quotidian and ubiquitous, whereas quantitative talk implies the notion of a probability function.
+It might be the case that speakers use it `innocently' without recourse to probability theory, but it's a different question of whether they do so competently.
+We argue that they might as well don't.
+The result is that the criterion does not necessarily help us evaluate adequate semantics for likelihood talk, and thus will be excluded from the present considerations.
+
 \section{Kratzer's Preferential Semantics}
@@
 
-Kratzer is unhappy with what she calls the \emph{standard analysis} as is gives the wrong verdict in two salient scenarios.
---maybe also go through kratzer's examples which further motivate her decisions--maybe explain why we don't have an even easier definition.
+Kratzer is unhappy with what she calls the \emph{standard analysis} as it gives the wrong verdict in two salient scenarios.
+These are concerned with conflicting rules of law and an a combination of indicative conditionals and modals, respectively.
+We will not reiterate these scenarios here, but--spoiler alert--Kratzer's theory manages to do them justice.
 
-Importantly, the account for modality needs to include graded modalities, of the following sort:
+More relevantly, the account for modality according to Kratzer needs to include graded modalities, of the following sort:
 \begin{enumerate}[nosep,label=\alph*)]
@@
 \end{enumerate}
-Here, the modalities are listed in decreasing strength, such that the intended
-reading is that a) implies b), b) implies c), and so forth.
-Note that is a qualitative approach to graded modals, as opposed to quantitative approaches, employing a scale structure in the semantics.
+Here, the modalities are listed in decreasing strength, such that the intended reading is that a) implies b), b) implies c), and c) implies d).
+Note that is a qualitative approach to graded modals, as opposed to quantitative approaches, employing a scale structure in the semantics, as described by \textcite{lassiter10_gradab}.
 
@@
 \item Neatly fits with the other modals, just change f and g
-\item Gives an account of probable without resorting to probability measures (give argument by Hamblin - maybe more in philosophy texts? check titelbaum)
-\item solves problems describes in Kratzer text (probably dont reiterate)  
-\end{itemize}
+\item Gives an account of probable without resorting to probability functions (give argument by Hamblin - maybe more in philosophy texts? check titelbaum)
+\end{itemie}
 }
 How do the semantics look like?
-we assume a set $W$ of possible worlds, a set of propositions $P$ such that elements of $P$ are subsets of $W$, and assume that a proposition $p$ is true at $w$ iff $w \in p$.
+We assume a set $W$ of possible worlds, a set of propositions $P$ such that elements of $P$ are subsets of $W$, and assume that a proposition $p$ is true at $w$ iff $w \in p$.
 The crucial element in Kratzer's semantics that distinguishes her account from most simple semantics via Kripke frames with an accessibility relation is the \emph{conversational background}.
@@
 
+\todo{FORMALIZE MIGHT PHI}
 \subsection{Discussion}
@@
 \section{Hamblin's Possibility Semantics}
-\todo{
-  \begin{itemize}
-    \item Write an Introduction and Purpose compared to Kratzer
-  \end{itemize}}
+Already in the 1950's, \textcite{hamblin59_modal_probab} developed a semantics for the \emph{probable}-operator based on what he called plausibility and more recently is referred to as possiblity.
+Possibility functions are quite similar to probability functions, but do not require finite additivity.
+They have been used to model an agent's belief state when the focus is on modeling the agent's surprise as well as ignorance towards some proposition.
+They are useful in modeling vagueness and have the advantage over probability functions that the possibility of the union of two propositions is uniquely determined by the marginal possibilities of the propositions, while probabilities only provide bounds unless the propositions are disjoint \parencite[][p.~45]{halpern03_reason_about_uncer}.
+
+Why should possibilities be particularly appropriate in semantics?
+Hamblin does not present a clear argument, but refers to that the weighing of reasons is captured better in possibilities than in probabilities \parencite[][p.~240]{hamblin59_modal_probab}.
+Yalcin gives his interpretation of Hamblin as that probabilities are too idealized, and possibilities provide a less restricted formal structure and are thus more appropriate to model everyday likelihood talk.
+In any case, let us look at the formal setup and evaluate whether Hamblin's account holds up to our criteria. 
+The account presented here is a reinterpretation based on \textcite{hamblin59_modal_probab}, \textcite[][pp.~42]{halpern03_reason_about_uncer} and \textcite{yalcin10_probab_operat} to fit the account into contemporary semantics.
+
 \subsection{Formal Setup}
@@
   \item $\emptyset, W \in \F$,
-  \item $A \in \F \Rightarrow \bar{A} \in \F$
-  \item $A,B \in \F \Rightarrow A \cup B \in \F$
+  \item $A \in \F \Rightarrow \bar{A} \in \F$, and
+  \item $A,B \in \F \Rightarrow A \cup B \in \F$.
 \end{enumerate}
@@
 \begin{enumerate}[nosep]
-  \item $p(\emptyset) = 0$ 
-  \item $p(W) = 1$
-  \item $p(U \cup V) = \max(p(U),p(V))$
+  \item $p(\emptyset) = 0$,
+  \item $p(W) = 1$, and
+  \item $p(U \cup V) = \max(p(U),p(V))$.
 \end{enumerate}
-Following \textcite{hamblin59_modal_probab},
-\textcite[][pp.~42]{halpern03_reason_about_uncer} and Yalcin's
-\parencite*{yalcin10_probab_operat} reinterpretation to fit Hamblin's account into modern
-semantics, we define the following: 
 \begin{definition}

### 2019-03-24 paper.tex
fleshed out middle sections
finishing the formal details

@@
 \usepackage[utf8]{inputenc}
+
+% \usepackage{aaai}
+% \usepackage{times}
+% \usepackage{helvet}
+% \usepackage{courier}
+
 \usepackage{amsmath}
@@
 Whether some formally specified semantics validates a given inference pattern is then simply not a matter of debate and can be shown mathematically given the assumptions one is forced to make explicit.
+The rules are not meant to characterize a logic, of course.
 \todo{
@@
 \begin{prooftree}
-    \hypo{ \varphi \succeq \neg \varphi } \infer1[(I2)]{ \varphi \succeq \psi}
+    \hypo{ \varphi \succeq \neg \varphi } \hypo{ \neg \varphi \succeq \varphi}\infer2[(I2)]{ \varphi \succeq \psi}
     \end{prooftree}
@@
 The result is that the criterion does not necessarily help us evaluate adequate semantics for likelihood talk, and thus will be excluded from the present considerations.
+
+Yalcin also discuss criteria concerning the combination of epistemic modals and indicative conditionals (V8-V10, not listed here).
+While undoubtedly very interesting, also considering semantics for conditionals and integrating those with epistemic modal semantics would be beyond the scope of this short paper.
+
+Also not considered in this paper are more advanced discussions of intuitive validity of \emph{probable}-judgments. One example is a lottery with 1000 possible tickets.
+Suppose Bloggs has 420 tickets, and 580 other players have one ticket each \parencite[p.~931]{yalcin10_probab_operat}. Is the following true or false?
+`Probably, Bloggs is the winner of the lottery'.
+Although the chance of Bloggs winning is less than him not winning, intuitions here are apparently mixed.
+Throughout this paper, however, we assume that `probably $\varphi$' is equivalent to `$\varphi$ is more probable than not', ignoring the problematic intuitions just described.
 
@@
 \item Gives an account of probable without resorting to probability functions (give argument by Hamblin - maybe more in philosophy texts? check titelbaum)
-\end{itemie}
+\end{itemize}
 }
@@
 Assuming here that we are looking at a flat fragment and $\alpha$ doesn't contain modals itself.
-Intuitively,... [briefly explain]
+Intuitively,... \todo{[briefly explain]}
 
@@
 Kratzer's account does \emph{not} validate (V11-V12).
+
+\todo{THE FOLLOWING IS NOT CORRECT AND NEEDS TO BE REDONE}
 \textcite[pp.~935, note~8]{yalcin10_probab_operat} gives a countermodel.
@@
     \label{def:hambsem}
-    Let $M = \langle M,R,V,\mathcal{F},\Pr \rangle$ be a Hamblin possiblity model, $w \in W$, $\varphi, \psi \in \L$.
-We define clauses 1-4 just like in Kratzer preferential semantics (Definition \ref{def:kratsem}).
+    Let $M = \langle M,R,V,\mathcal{F},\Po \rangle$ be a Hamblin possiblity model, $w \in W$, $\varphi, \psi \in \L$.
+We define clauses 1-4 and 6 just like in Kratzer preferential semantics (Definition \ref{def:kratsem}).
 We define further:
     \begin{enumerate}[nosep]
-  \setcounter{enumi}{5}
-      \item $M,w \models \varphi \succeq \psi$ iff $p_w(\lb \varphi \rb^M) \geq p_w(\lb \psi \rb^M) $
-      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ \neg \varphi$ 
+  \setcounter{enumi}{4}
+      \item $M,w \models \varphi \succeq \psi$ iff $p_w(\lb \varphi \rb^M) \geq p_w(\lb \psi \rb^M) $,
+  \setcounter{enumi}{6}
+  \item $M,w \models \Diamond \varphi$ iff there is a $w' \in R(w)$ such that $ M,w' \models \varphi$.
     \end{enumerate}
 \end{definition}
+\noindent Here, we added a the standard semantics for $\Diamond \varphi$, as Yalcin proposes.
+That the model contains a function assigning each world another function might seem formal overkill at first, but is just there such that the possiblity judgments are properly world-relative.
+When focusing on other aspects and e.g.
+developing a logic for this semantics, we might simplify our model in this regard, as \textcite{harrison-trainor17_prefer} do with preferential and probability models.
+
 \subsection{Discussion}
-\todo{
-  \begin{itemize}
-    \item Write Discussion
-  \end{itemize}
-}
+
+Hamblin's account satisfies (V1-V7), as can easily be seen. For example, let us briefly validate (V2) like for Kratzer's account.
+Suppose $M,w \models \triangle(\varphi \land \psi)$, hence $p_w(\lb(\varphi \land \psi )\rb^M) > p_w(\lb \neg (\varphi \land \psi) \rb^M)$.
+Because $p_w(\lb (\varphi \land \psi)\rb^M \cup {\lb\neg(\varphi \land \psi)\rb^M)} = 1$, by (2) and (3) of the definition of possibility functions, we have $p_w(\lb (\varphi \land \psi) \rb^M) = 1$.
+If $W$ is finite, there is $w' \in \lb (\varphi \land \psi) \rb^M$ such that $p_w(\{w'\}) = 1$.
+Since $w'$ is in $\lb \varphi \rb^M$ and $\lb \psi \rb^M$, but there is no $w'' \in \lb \varphi \rb^M\setminus\lb \psi \rb^M$ or $\lb \psi \rb^M\setminus\lb \varphi \rb^M$ with $p_w(\{w''\}) = 1$ we have $p_w(\lb \varphi \rb^M) > p_w(\lb \neg \varphi \rb^M)$ and $p_w(\lb \psi \rb^M) > p_w(\lb \neg \psi \rb^M)$ and hence $M,w \models \triangle \varphi \land \triangle \psi$.
+
+Further, Hamblin validates pattern (V11-V12) \parencite[][p.~926]{yalcin10_probab_operat}.
+Like Kratzer, though, Hamblin also validates (I1) and (I2), but more egregiously, even (I3): 
+\begin{center}
+\begin{prooftree}
+    \hypo{ \triangle \varphi } \infer1[(I3)]{ \varphi \succeq \psi}
+    \end{prooftree}
+\end{center}
+To see this, note the fact we made use of above already: If $M,w \models \triangle \varphi$, then because $\lb \varphi \rb^M \cup \lb \neg \varphi \rb^M = W$, we have by (2) and (3) of the definition of possibility functions that $p_w(\lb \varphi \rb^M) = 1$ such that $M,w \models \varphi \succeq \psi$ for any $\psi \in \L$.
+This clearly runs counter to the idea of modeling the graded epistemic modal \emph{probable} in natural language.
+For other uses as in fuzzy logic \parencite[][p.~43]{halpern03_reason_about_uncer} this does of course say nothing.
 \section{Yalcin's Probability Semantics}
 
-\todo{
-  \begin{itemize}
-    \item Write Introduction
-  \end{itemize}
-}
+Unsatisfied with the accounts described so far, Yalcin proposes to overcome the wariness towards probability functions as semantics for probability talk.
+The semantics developed by \textcite{yalcin10_probab_operat} and very similarly by \textcite{lassiter10_gradab} is the absolutely straightforward application of probability measures towards our present problem, so obvious in fact that it strikes me as noteworthy that these seem to be among the earliest applications of probability functions to \emph{probable}-talk, as both Yalcin and Lassiter claim.
+The following definitions are quite unsurprising, then.
 \subsection{Formal Setup}
@@
     Let $M = \langle M,R,V,\mathcal{F},\Pr \rangle$ be a Yalcin probability model, $w \in W$, $\varphi, \psi \in \L$.
-We define clauses 1-3 just like in Kratzer preferential models (Definition \ref{def:kratsem}).
+We define clauses 1-4 just like in Kratzer preferential models (Definition \ref{def:kratsem}).
 We define further:
@@
   \setcounter{enumi}{4}
-      \item $M,w \models \varphi \succeq \psi$ iff $\mu_w(\lb \varphi \rb^M) \geq \mu_w(\lb \psi \rb^M) $
-      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ^{M,w} \neg \varphi$ iff $ \mu_w(\lb \varphi \rb^M) > .5$
+      \item $M,w \models \varphi \succeq \psi$ iff $\mu_w(\lb \varphi \rb^M) \geq \mu_w(\lb \psi \rb^M) $,
+      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ^{M,w} \neg \varphi$ iff $ \mu_w(\lb \varphi \rb^M) > .5$, and
+  \item $M,w \models \Diamond \varphi$ iff there is a $w' \in R(w)$ such that $ M,w' \models \varphi$.
     \end{enumerate}
@@
 \subsection{Discussion}
-\todo{
-  \begin{itemize}
-    \item Write Discussion
-  \end{itemize}
-}
+
+Yalcin promotes his account as satisfying all criteria (V1-V7), (V11-V12), (I1-I3) we defined.
+Let's look at some of them. 
+To compare, the probability semantics validate V2: Suppose $M,w \models
+\triangle(\varphi \land \psi)$. Then $\mu_w(\lb \varphi \land \psi\rb^M) > .5$.
+Since marginal probabilities are bounded from below by joint probabilities of
+the same variable, we have $\mu_w(\lb \varphi \rb^M) > .5$ and hence $M,w
+\models \triangle \varphi$. The case for $\psi$ is analogous.
+The semantics satisfy (I1) by invalidating the pattern.
+\begin{center}
+\begin{prooftree}
+    \hypo{ \varphi \succeq \psi } \hypo{\varphi \succeq \chi}\infer2[(I1)]{ \varphi \succeq (\psi \lor \chi)}
+    \end{prooftree}
+\end{center}
+
+\noindent To see this, fix a model $M$ and a world $w \in W$ (sub- and superscripts suppressed).
+Let $\mu(\lb\varphi\rb) = .6;~ \lb\psi\rb \cap \lb\chi\rb=\emptyset;~ \mu(\lb\psi\rb) = \mu(\lb\chi\rb) = .4$. (that such a model exists can be easily verified).
+Then $\mu(\lb \psi \rb \cup \lb \chi \rb) = .8$.
+Thus $M,w \models \varphi \succeq \psi$ and $ M,w \models \varphi \succeq \chi$ but $M,w \not\models \varphi \succeq (\psi \lor \chi)$.
+
+Given our criteria, then, the probabilistic model is the clear winner.
+Does this
+mean preferential accounts in general are inapt to model the
+\emph{probable}-talk semantics?
+Not quite, as we will see in the next section.
+
 \section{Holliday and Icard's Preferential Semantics}
-\todo{
-  \begin{itemize}
-    \item Write Introduction
-  \end{itemize}
-}
+
+\textcite{holliday13_measur} are not yet ready to accept defeat for the preferentialist.
+First, they set out to generalize Yalcin's account and replace probability functions with so called qualitatively additive measures \parencite[][p.~522]{holliday13_measur}, which they show to also be adequate with respect to our criteria.\footnote{It is noteworthy that they describe (I2) as `If $\varphi \succeq \neg \varphi$ then $\varphi \succeq \psi$', instead of the present version (see above), since the resulting claims are different.
+It could be worthwile to investigate further where this discrepancy is coming from.}
+They also briefly consider an ordering directly on the set of propositions instead of inducing the order from an order on worlds, and state that here, one can quite straightforwardly constrain the ordering such that it provides a semantic to satisfy the adequacy criteria \parencite[p.~924]{holliday13_measur}.
+They dismiss it, however, because it is more desirable to not have a primitive order on propositions.
+It seems they are themselves doubting this point and merely reiterate an established point.\footnote{This, too, seems worth investigating further.}
+
 \subsection{Formal Setup}
@@
 What about the $\epsilon$-semantics (Adams, Pearl)?
+
 \nocite{hamblin59_modal_probab,holliday13_measur,harrison-trainor17_prefer,kratzer91_modal,lassiter10_gradab,yalcin10_probab_operat,kratzer98_seman}

### 2019-03-24 paper.tex
formal part in beta mode, now write introduction

@@
 \documentclass{article}
-\title{The Epistemic Modal \emph{probable}}
-\author{Conrad Friedrich \\ MCMP, LMU Munich }
-\date{\today}
-
 \usepackage[utf8]{inputenc}
@@
 \newcommand{\succeqK}{\succeq^K_{M,w}}
+\newcommand\wordcount{\input{paper.sum}}
+
+\title{The Epistemic Modal \emph{probable}}
+\author{Conrad Friedrich \\ MCMP, LMU Munich \\ \wordcount words}
+\date{\today}
+
 \begin{document}
@@
 }
-\section{Intensional Semantics}
-\todo{ \begin{itemize}[nosep]
-  \item Tie the paper into framework used in class
-\end{itemize} }
 
-Note that we don't need first order logic. 
-Abstracted away from syntax, just look at the semantics.
-NEAT summary in Ivano's script, Class 9, page 3/4
+\subsection{Intensional Semantics}
+In this paper, we will not be concerned with type theoretical considerations.
+It seems also that the relevant literature is not very keen on discussion that.
+One reason might be that it is rather simple.
+We just view the \emph{probable}-operator as an operator on sentences, such that we just add something along the lines of `if $\varphi:t$ then $\triangle \varphi:t$' to our type theory.
+The interesting developments for the purposes of this paper take place when we enrich the model for our calculus.
+As a further simplification, we will only be concerned with a simple propositional language to not add further complexity by considering first order models, as will be described in the next section.
+
 \section{The Epistemic Modal \emph{probable}}
@@
 \[
-\varphi ::= p ~|~ \neg \varphi ~|~ (\varphi \land \psi) ~|~  (\varphi \succeq \psi) ~|~ \triangle\varphi ~|~ \Diamond \varphi
+\varphi ::= p ~|~ \neg \varphi ~|~ (\varphi \land \psi) ~|~  (\varphi \succeq \psi) ~|~ \triangle\varphi 
 \]
-Where $p \in \text{Atom}$, i.e. an atomic formula. The other boolean connectives $(\varphi \rightarrow \psi), (\varphi \vee
+Where $p$ is an atomic formula, i.e. $p \in \text{Atom}$. The other boolean connectives $(\varphi \rightarrow \psi), (\varphi \vee
 \psi)$ as well as $\top, \bot$ are defined in the standard way from negation and conjunction.
-Define further $\Box \varphi = \neg\Diamond\neg \varphi$.
 The intended readings are as follows:
@@
   \triangle \varphi &:\text{probably } \varphi. \\ 
-                      \Diamond \varphi &: \text{It might be that } \varphi.
 \end{align*}
@@
 The rules are not meant to characterize a logic, of course.
+
 \todo{
@@
   \item Motivate and describe the conditions
+  \item Describe what inference means (truth preservation)
 \end{itemize}
@@
     \hypo{ } \infer1[(V5)]{ \top \succeq \varphi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \Box \varphi } \infer1[(V6)]{ \triangle \varphi}
-    \end{prooftree}
-\end{center}
-
-\begin{center}
-\begin{prooftree}
-    \hypo{ \triangle \varphi } \infer1[(V7)]{ \Diamond \varphi}
     \end{prooftree}
@@
 
+In addition, we weren't able to include formal considerations on how \emph{probable}-talk relates to other epistemic modals like \emph{might, must}, etc., due to time and place constraints, although this aspect is particularly lending itself to analysis and would be the first to consider in a longer paper.
+
 \section{Kratzer's Preferential Semantics}
-\todo{
-  \begin{itemize}
-    \item Clean up this section a bit
-  \end{itemize}
-}
 For \textcite{kratzer91_modal} epistemic modals like \emph{probably} are just a special case of a more general class of modal auxiliaries.
@@
 
-Kratzer postulates that modality is always relative to a certain kind of interpreting the modalities involved, following Peirce (cite).
-She set out to formulate these different modalities in a common framework such that we'd only need to specify some parameters of the framework to determine the relevant modalities and give truth conditions for sentences involving modalities, while focussing on epistemic modals.
+Kratzer postulates that modality is always relative to a certain kind of interpreting the modalities involved.
+She sets out to formulate these different modalities in a common framework such that we'd only need to specify some parameters of the framework to determine the relevant modalities and give truth conditions for sentences involving modalities, while focusing on epistemic modals.
 
@@
 Here, the modalities are listed in decreasing strength, such that the intended reading is that a) implies b), b) implies c), and c) implies d).
-Note that is a qualitative approach to graded modals, as opposed to quantitative approaches, employing a scale structure in the semantics, as described by \textcite{lassiter10_gradab}.
+Note that is a qualitative approach to graded modals, as opposed to quantitative approaches. Some of these employ a scale structure in the semantics, as described by \textcite{lassiter10_gradab}.
 
-\todo{\begin{itemize}[nosep]
-  \item The account presented has a couple of advantages.
-\item Neatly fits with the other modals, just change f and g
-\item Gives an account of probable without resorting to probability functions (give argument by Hamblin - maybe more in philosophy texts? check titelbaum)
-\end{itemize}
-}
+Kratzer intends her account to fit into a common framework for other gradable modals.
+The idea is to just change the parameters $f,g$--to be introduced shortly--to represent the constraints that different modalities impose upon the semantics.
+If successful, this idea would come out in favor of Kratzer's account, since it unifies multiple semantics into a single formal framework.
+In addition, we'd have semantics for epistemic modals and \emph{probable}-talk that do not need to make recourse to probability theory.
+Whether these two features actually do speak in favor of Kratzer's account shall not be evaluated in this paper and are just now mentioned.
+We stick to the criteria defined in the beginning.
+
 How do the semantics look like?
-We assume a set $W$ of possible worlds, a set of propositions $P$ such that elements of $P$ are subsets of $W$, and assume that a proposition $p$ is true at $w$ iff $w \in p$.
-The crucial element in Kratzer's semantics that distinguishes her account from most simple semantics via Kripke frames with an accessibility relation is the \emph{conversational background}.
+We assume a set $W$ of possible worlds, propositions are subsets of $W$, and assume that a proposition $p$ is true at $w$ iff $w \in p$.
+The crucial element in Kratzer's semantics that distinguishes her account from most simple semantics via Kripke frames with only a single accessibility relation is the \emph{conversational background}.
 It has two components.
@@
 The \emph{modal base} determines for every world the set of worlds which are epistemically accessible from it.
-More formally, the modal base is a function $f: W \rightarrow \wp(W)$ assigning each world $w$ a set of worlds.
-The set of worlds $f(w)$ assigned to $w$ represents, in the epistemic case, what we know at $w$.
+More formally, the modal base is a function $f: W \rightarrow \wp(W)$ assigning each world $w$ a set of worlds.\footnote{It is not perfectly clear from \textcite[][p.~644]{kratzer91_modal}, but it seems that the modal base in fact assigns a set of propositions to each world, so a set of sets of worlds.
+This is as far as we can tell equivalent for our purposes to the definition proposed here, if we make slight amendments.}
+The set of worlds $f(w)$ assigned to $w$ is intended to represent what we know at $w$.
 
@@
 \cite{lewis81_order_seman_premis_seman_count}).
-The ordering source induces an order $\leq_{g(w)}$ on $W$ for all $w,w' \in W$ as follows:
-\begin{equation}
-    \label{eq:porder}
-w \leq_{g(w)} w' :\iff \{p: p\in g(w) ~\&~ w' \in p\} \subseteq \{p: p\in  g(w) ~\&~ w \in p\}
-\end{equation}
-\todo{THIS NEED UPDATING SINCE g(w) CHANGED!}
+The ordering source induces an ordering $\leq_{g(w)}$ on $W$ for all $w,w' \in W$ as follows:
+% \begin{equation}
+%     \label{eq:porder}
+% w \leq_{g(w)} w' :\iff \{p: p\in g(w) ~\&~ w' \in p\} \subseteq \{p: p\in  g(w) ~\&~ w \in p\}
+% \end{equation}
+% \todo{THIS NEED UPDATING SINCE g(w) CHANGED!}
 \begin{equation}
@@
 From this, Kratzer defines a the semantics for a list of different expressions, like `good possibility', `possibility' and so on.
-For our purposes, it suffices to look at those definitions involved in defining the meaning of \emph{probably $\alpha$}.
+For our purposes, it suffices to look at the following ordering on propositions:
 
-First, define `as least as good a possibility as'.
-The induced order on worlds $\leq_{g(w)}$ is `lifted' to an order on the level of propositions.
+The induced ordering on worlds $\leq_{g(w)}$ is `lifted' to an ordering on the level of propositions.
 For a modal base $f$ and a ordering source $g$, for propositions $A,B$ and world $w$, we can define
@@
 
-The strict part is defined as one would expect:
-
-\noindent $A \succ_w B :\iff {A \succeq_w B ~\&~ B \not\succeq_w A}$.
-
-Finally, we can assign a meaning to \emph{probably $\alpha$} given a set of worlds $W$, a modal base $f$ and a ordering source $g$ \parencite[][p.~645]{kratzer91_modal}:
-\begin{equation}
-\llbracket \text{probably } \alpha \rrbracket^{f,g,w} = 1 :\iff \lb \alpha \rb \succ_w \lb \neg\alpha \rb
-\end{equation}
-Assuming here that we are looking at a flat fragment and $\alpha$ doesn't contain modals itself.
-Intuitively,... \todo{[briefly explain]}
+In the next section, we describe how this ordering can be used to define a semantics for our propositional language.
 
@@
 
-To put it slightly more formally, we define: 
 \begin{definition}
@@
 Further, we want the induced order defined above also hold for $M$.
-This is done in the following uninteresting definition:
-Let $f$ be a modal base, $g$ be a ordering source, $W$ a set of worlds.
-For each $w \in W$ let $\succeq_w$ be the order on subsets of $W$ defined in
-Equation \ref{eq:lifted}.
+This is done via the following rather obvious definition:
 Let $M = \langle W,f,g,V \rangle$ be a Kratzer preferential model.
-For $p,q \subseteq W$ we define an induced order on $\wp(W)$:   
+For each $w \in W$ let $\succeq_w$ be the order on $\wp(W)$ defined in Equation \ref{eq:lifted}.
+For $A,B \subseteq W$ we then define:   
 \begin{equation}
     \label{eq:induced}
-       p \succeq^{M,w} q \text{ iff } p \succeq_w q.
+       A \succeq^{M,w} B \text{ iff } A \succeq_w B.
 \end{equation}
@@
       \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succeq \neg \varphi ~\&~ \neg (\neg \varphi \succeq \varphi)$,
-      \item $M,w \models \Diamond \varphi$ iff ...
     \end{enumerate}
@@
 
-\todo{FORMALIZE MIGHT PHI}
 \subsection{Discussion}
@@
 How does Kratzer's account fare with respect to the adequacy conditions we defined?
-The semantics validate conditions (V1-V7), which can be easily seen by applying the definitions.
+The semantics validate conditions (V1-V5), which can be easily seen by applying the definitions.
 For example, let us establish that Kratzer preferential semantics satisfy (V2), i.e.: 
@@
 
-Kratzer's account does \emph{not} validate (V11-V12).
-
-\todo{THE FOLLOWING IS NOT CORRECT AND NEEDS TO BE REDONE}
-\textcite[pp.~935, note~8]{yalcin10_probab_operat} gives a countermodel.
+Kratzer's account does \emph{not} validate (V11-V12). \textcite[pp.~935, note~8]{yalcin10_probab_operat} gives a countermodel.
 In addition, the account \emph{does} validate pattern (I1), as can easily be seen.
@@
 Additionally, (I1) together with (V5) entails (I2) \parencite[p.~922]{yalcin10_probab_operat}.
-That is, on this account, anything that is probable is a least as likely as any tautology.
-This is, of course, a ruinous result.
+That is, on this account, anything that is as probable as its negation is at least as likely as any tautology.
+This is, one can argue, a ruinous result.
+
+Let's have a look at different accounts and see whether they fare better.
 
@@
         \item $V$ is a function $V: \text{Atom} \rightarrow \wp(W)$,
-        \item $\mathcal{F}$ is a function assigning each world $w \in W$ a boolean algebra $\F_w$ on $R(w)$, and 
+        \item $\mathcal{F}$ is a function assigning each world $w \in W$ a boolean algebra $\F_w$ on $R[w]$, and 
           \item $\Po$ is a function assigning each world $w \in W$ a possibility function \\ $p_w: \F_w \rightarrow [0,1]$.
@@
   \setcounter{enumi}{6}
-  \item $M,w \models \Diamond \varphi$ iff there is a $w' \in R(w)$ such that $ M,w' \models \varphi$.
     \end{enumerate}
 \end{definition}
-\noindent Here, we added a the standard semantics for $\Diamond \varphi$, as Yalcin proposes.
 That the model contains a function assigning each world another function might seem formal overkill at first, but is just there such that the possiblity judgments are properly world-relative.
@@
 
-Hamblin's account satisfies (V1-V7), as can easily be seen. For example, let us briefly validate (V2) like for Kratzer's account.
+Hamblin's account satisfies (V1-V5), as can easily be seen. For example, let us briefly validate (V2) like for Kratzer's account.
 Suppose $M,w \models \triangle(\varphi \land \psi)$, hence $p_w(\lb(\varphi \land \psi )\rb^M) > p_w(\lb \neg (\varphi \land \psi) \rb^M)$.
@@
         \item $V$ is a function $V: \text{Atom} \rightarrow \wp(W)$,
-        \item $\mathcal{F}$ is a function assigning each world $w \in W$ a boolean algebra $\F_w$ on $R(w)$, and 
+        \item $\mathcal{F}$ is a function assigning each world $w \in W$ a boolean algebra $\F_w$ on $R[w]$, and 
           \item $\Pr$ is a function assigning each world $w \in W$ a probability function \\ $\mu_w: \F_w \rightarrow [0,1]$.
@@
       \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ^{M,w} \neg \varphi$ iff $ \mu_w(\lb \varphi \rb^M) > .5$, and
-  \item $M,w \models \Diamond \varphi$ iff there is a $w' \in R(w)$ such that $ M,w' \models \varphi$.
     \end{enumerate}
@@
 
-Yalcin promotes his account as satisfying all criteria (V1-V7), (V11-V12), (I1-I3) we defined.
+Yalcin promotes his account as satisfying all criteria (V1-V5), (V11-V12), (I1-I3) we defined.
 Let's look at some of them. 
@@
 
+Finally, they propose an amendment to Kratzer's preferential semantics, intended to resolve the issues noted by Yalcin and Lassiter.
+With a seemingly small change on how the ordering is lifted from worlds to propositions, they manage to achieve a host of desired effects.
+For example, while Kratzer's lifting creates a total ordering on propositions if the order on worlds is total, not so for Holliday and Icard's lifting (cf.
+\parencite[][p.~525]{holliday13_measur} for a nice extended argument for why this is desirable).
+We describe the precise change in the next section, and have a look at the results concerning our criteria after that.
+
 \subsection{Formal Setup}
@@
 \end{definition}
-Let $R[w] = \{w':wRw'\}$. For any proposition $P \subseteq W$, $P_w := P \cap R[w]$. Further, for two proposition $A,B \subseteq W$ we define
+For any proposition $P \subseteq W$, $P_w := P \cap R[w]$. Further, for two proposition $A,B \subseteq W$ we define
 \begin{multline}
@@
 \subsection{Discussion}
-\todo{
-  \begin{itemize}
-    \item Write Discussion
-  \end{itemize}
-}
+
+Holliday and Icard promote their account as satisfying all adequacy criteria (V1-V5), (V11-V12), (I1-I3).
+Let's have a closer look.
+First, as an example, the account again satisfies (V2).
+To show this, we can take the argument from Kratzer's semantics, and amend it slightly such that Holliday and Icard's condition (\ref{eq:injection}) is satisfied.  
+We will spare the reader such repetitious reading.
+
+We can instead employ the model Holliday and Icard provide to construct a countermodel to (I1).
+Recall that Kratzer's account validated this pattern.
+We adopt slightly sloppy notation to improve readability.
+
+Fix a model $M$ and a world $w$.
+Let $W = \{abcd\}$, ordered by $M$ like so: $a > b > c > d$.
+Let $A = \{ab\}, B = \{bc\}, C = \{cd\}$.
+It's easy to see that by (\ref{eq:injection}), we have $A \succ B \succ C$.
+However, we do not have $A \succ (B \cup C)$, since we can't construct an injection like required.
+Hence, (I1) is not validated.
+A clear improvement over Kratzer's semantics.
+
 \section{Conclusion}
+Maybe make an overview table from org mode
 \todo{

### 2019-03-24 paper.tex
Almost completely done. Enter beta

@@
 \usepackage{stmaryrd}
+\usepackage{textcomp}
 \usepackage{enumitem}
@@
 
-\todo{
-  \begin{itemize}[nosep]
-    \item Write an Introduction
-     \item be perfectly clear as to what happens. SIGNPOST 
-  \end{itemize}
-}
+What do we mean when we say something like `It is likely going to rain' or `I probably left my car keys at home'?
+This paper studies formal accounts which provide a semantical analysis of epistemic modals like \emph{likely} and \emph{probable}.
+Towards this goal, we survey the literature in philosophy and formal semantics proposing and evaluating such accounts.
+By establishing a list of criteria such an account should fulfill, we give a comprehensible and readily criticizable evaluation of the accounts.
+To make things easier to compare, we provide a common propositional language and define the semantics of the different accounts directly for this language.
+Thus the purpose of this paper is to make the accounts as transparently comparable as possible, and then evaluate them according to a set of specification.
 
-\subsection{Intensional Semantics}
+The literature provides a natural classification into qualitative and quantitative accounts of analyzing \emph{probable}-talk.
+We will see that both types of accounts provide adequate analysis according to the criteria we introduce.
+
+In order to introduce the topic, we introduce Kratzer's semantics a bit more extensively than in the subsequent presentations.
+
+The paper is structured as follows.
+First, we'll briefly introduce \emph{probable} in the context of epistemic modals.
+Then we will establish a set of criteria which a semantic theory for \emph{probable} should satisfy.
+We will discuss why these criteria and which additional criteria we decided to or had to leave out of this paper.
+In the subsequent sections, we will present and critically evaluate four different accounts for epistemic modals.
+Two of these are qualitative, two are quantitative in nature.
+For each of the accounts, we will first introduce the formal structure in some detail and then discuss the account according to our established criteria.
+We mostly follow \textcite{yalcin10_probab_operat} and \textcite{holliday13_measur} in our exposition.
+
+\subsection{Type Theory and Intensional Semantics}
+A quick word regarding the connection to type theory.
 In this paper, we will not be concerned with type theoretical considerations.
-It seems also that the relevant literature is not very keen on discussion that.
-One reason might be that it is rather simple.
-We just view the \emph{probable}-operator as an operator on sentences, such that we just add something along the lines of `if $\varphi:t$ then $\triangle \varphi:t$' to our type theory.
+It seems that also in the relevant literature authors are not very keen on discussing the connection.
+One reason might be that it is rather straightforward and uninteresting: here, we just view the \emph{probable}-operator as an operator on sentences, such that we merely add something along the lines of `if $\varphi:t$ then $\triangle \varphi:t$' to our type theory.
 The interesting developments for the purposes of this paper take place when we enrich the model for our calculus.
-As a further simplification, we will only be concerned with a simple propositional language to not add further complexity by considering first order models, as will be described in the next section.
+As a further simplification, we will only be concerned with a simple propositional language instead of a first order one.
 
 \section{The Epistemic Modal \emph{probable}}
-\todo{\begin{itemize}[nosep]
-    \item  Give some natural language motivation
-    \item Also show the need for expanding the standard intensional semantics!
-    \item How is probable to be evaluated? Epistemic interpretation? MacFarlane's Solipcism.
-    \item Mention how Lassiter has a different, graded adjective based approach.
-    \item Discuss how absolute probability is best reduced to relative likelihood with the negation
-      \item note that there are a lot more interesting problems associated with probable but to have an readable paper need to focus on particulars.
-  \end{itemize}
-}
+Epistemic modals are ubiquitous in everyday conversation.
+It is not entirely obvious, however, what exactly one expresses when exclaiming, e.g. `John can't be running!' after seeing his shoes not on the hook they are usually hanging.
+\textcite{macfarlane11_are_asses_sensit} offers the interpretation that these claims have to do with the speakers knowledge and what is compatible with it.
+`John can't be running' does not express a metaphysical impossibility, rather, it is incompatible with what the speaker knows or believes.
+This is what we'll adopt here, too.
+There are a host of interesting philosophical and linguistic problems associated with uttering sentences involving epistemic modals (cf.
+\cite{yalcin07_epist_modal}), which will mostly not be the focus of this paper.
+Rather, we will concern ourselves with analyzing \emph{probable}.
+The epistemic modal \emph{probable} is more nuanced and is subject to grading:
+something can reasonably be judged more or less probable. It comes in comparative (e.g. `$\varphi$ is at least as likely as $\psi$') and absolute (e.g. `probably $\varphi$') flavor.
+Throughout this paper, we will assume that both types are closely related: absolute \emph{probable}-talk is just comparative \emph{probable}-talk `in disguise'.
 
-To base the following discussions on a common language, we define a
-propositional language $\L$ like \textcite{harrison-trainor17_prefer} and
-\textcite{holliday13_measur} do:
+To base the following discussions on a common language, we define a propositional language $\L$ (cf. \cite{harrison-trainor17_prefer}):
 \[
@@
 Whether some formally specified semantics validates a given inference pattern is then simply not a matter of debate and can be shown mathematically given the assumptions one is forced to make explicit.
-The rules are not meant to characterize a logic, of course.
+The rules are not meant to characterize a logic, of course. Let us briefly go through all criteria we evaluate the accounts by in this paper.
+The criteria are stated in the form of inference patterns. The inferences here can just be understood as classical truth preservation.
 
-\todo{
-\begin{itemize}[nosep]
-  \item Motivate and describe the conditions
-  \item Describe what inference means (truth preservation)
-\end{itemize}
-}
+We follow \textcite{yalcin10_probab_operat} quite closely in the rest of this subsection.
+
+What do we mean by \emph{valid} in the following? We refer here to intuitively reasonable inference patterns. We ascribe a competent speaker of English to agree in validating or rejecting a pattern.
+
+Patterns (V1-V5) are clearly valid:
+Intuitively, it's clear that not both a proposition and its negation should be considered probable, expressed in (V1).
+(V2) claims that if a conjunction is probable, both of its conjuncts must be, too.
+Since a disjunction shouldn't be less probable than either of its disjuncts, (V3) also is intuitively valid.
+
 \begin{center}
@@
 \end{center}
-
 \begin{center}
@@
 \end{center}
+
+\noindent Clearly, no proposition should be less likely than a contradiction, as (V4) states, or more likely than a tautology, as (V5) states.
 
@@
 
+\noindent (V11) states that if $\varphi$ is probable, and $\psi$ is more likely than $\varphi$, $\psi$ should be probable, too. This is clearly valid.
 \begin{center}
@@
 
+\noindent (V12) is less obvious, but still intuitively valid.
 \begin{center}
@@
 
+\noindent The concluding three patterns are intuitively invalid. Yalcin offers the following counterexample to (I1) when throwing a coin, which is clearly problematic.
+\begin{quote}
+   Heads is at least as likely as tails. Heads is at least as likely as heads. So, heads is at least as likely as heads or tails. 
+\end{quote}
+
 \begin{center}
@@
 \end{center}
+
+(I2) and (I3) are even more obviously undesirable. But some semantics, as we will see, still validate these patterns.
 
@@
 \section{Kratzer's Preferential Semantics}
+
 For \textcite{kratzer91_modal} epistemic modals like \emph{probably} are just a special case of a more general class of modal auxiliaries.
@@
 \section{Conclusion}
-Maybe make an overview table from org mode
-\todo{
-  \begin{itemize}
-    \item Write Conclusion and further studies
-  \end{itemize}
-}
-What about the $\epsilon$-semantics (Adams, Pearl)?
+\begin{figure}
+\begin{center}
+\begin{tabular}{lcccc}
+ & Kratzer & Hamblin & Yalcin & Holliday \& Icard\\
+\hline
+V1 & \(\checkmark\) & \(\checkmark\) & \(\checkmark\) & \(\checkmark\)\\
+V2 & \(\checkmark\) & \(\checkmark\) & \(\checkmark\) & \(\checkmark\)\\
+V3 & \(\checkmark\) & \(\checkmark\) & \(\checkmark\) & \(\checkmark\)\\
+V4 & \(\checkmark\) & \(\checkmark\) & \(\checkmark\) & \(\checkmark\)\\
+V5 & \(\checkmark\) & \(\checkmark\) & \(\checkmark\) & \(\checkmark\)\\
+\hline
+V11 & \texttimes{} & \(\checkmark\) & \(\checkmark\) & \(\checkmark\)\\
+V12 & \texttimes{} & \(\checkmark\) & \(\checkmark\) & \(\checkmark\)\\
+\hline
+I1 & \texttimes{} & \texttimes{} & \(\checkmark\) & \(\checkmark\)\\
+I2 & \texttimes{} & \texttimes{} & \(\checkmark\) & \(\checkmark\)\\
+I3 & \(\checkmark\) & \texttimes{} & \(\checkmark\) & \(\checkmark\)\\
+\end{tabular}
+\end{center}
+\caption{Overview of which account satisfies which criteria. Note that for
+  (I1-I3), `$\checkmark$' represents the account \emph{invalidating} that pattern.}
+\label{fig:table}
+\end{figure}
+In this paper, we compared different accounts for semantics of
+\emph{probable}-talk. The criteria we established were not satisfied by
+Kratzer's or Hamblin's account. Since Yalcin's (and also Lassiter's) probability
+semantics satisfy all criteria, it looked like the debate between preferential
+and probabilistic or qualitative and quantitative semantics had been settled
+with regards to the criteria. But Holliday and Icard improved on Kratzer's
+account such that it, too, satisfied the criteria. Thus at least from this
+vantage point, both types of semantics are able to make valuable contributions
+to explaining what we mean by \emph{probable}. An summarizing overview is
+provided in Figure \ref{fig:table}.
 
-\nocite{hamblin59_modal_probab,holliday13_measur,harrison-trainor17_prefer,kratzer91_modal,lassiter10_gradab,yalcin10_probab_operat,kratzer98_seman}
+Of course, this paper only scratches the surface of this topic. First, we
+severely limited the choice of criteria. Much more can be said as to how
+\emph{probable}-talk interfaces with other modals like \emph{might} or
+\emph{must}, or with indicative conditionals. We did not address the related
+discussion of graded modals and semantics on a scale like in Kennedy 2007 (look
+up reference in Lassiter). What's more, there is a host of interesting further
+work by \textcite{holliday13_measur} and \textcite{harrison-trainor17_prefer} ...
+\todo{Finish this section}
+
  \printbibliography

### 2019-03-25 paper.tex
RC1

@@
 
-\onehalfspacing
+% \onehalfspacing
 
@@
 \tableofcontents
+\newpage
 \section{Introduction}
@@
 What do we mean when we say something like `It is likely going to rain' or `I probably left my car keys at home'?
-This paper studies formal accounts which provide a semantical analysis of epistemic modals like \emph{likely} and \emph{probable}.
+This paper studies formal accounts which provide a semantical analysis of epistemic modals such as \emph{likely} and \emph{probable}.
 Towards this goal, we survey the literature in philosophy and formal semantics proposing and evaluating such accounts.
-By establishing a list of criteria such an account should fulfill, we give a comprehensible and readily criticizable evaluation of the accounts.
+By establishing a list of criteria, we give a comprehensible and readily criticizable evaluation of the accounts.
 To make things easier to compare, we provide a common propositional language and define the semantics of the different accounts directly for this language.
@@
 
-The literature provides a natural classification into qualitative and quantitative accounts of analyzing \emph{probable}-talk.
-We will see that both types of accounts provide adequate analysis according to the criteria we introduce.
+The literature provides a natural classification into qualitative and quantitative analyses of \emph{probable}-talk.
+We will see that both types are adequate according to the criteria we establish.
 
-In order to introduce the topic, we introduce Kratzer's semantics a bit more extensively than in the subsequent presentations.
+In order to introduce the topic, we present Kratzer's semantics a bit more extensively than in the subsequent presentations.
 
@@
 Then we will establish a set of criteria which a semantic theory for \emph{probable} should satisfy.
-We will discuss why these criteria and which additional criteria we decided to or had to leave out of this paper.
-In the subsequent sections, we will present and critically evaluate four different accounts for epistemic modals.
-Two of these are qualitative, two are quantitative in nature.
-For each of the accounts, we will first introduce the formal structure in some detail and then discuss the account according to our established criteria.
+We will discuss why these criteria are apt and which additional criteria we had to leave out of this paper.
+In the subsequent sections, we will present and critically evaluate four different accounts.
+Two of these are qualitative; two are quantitative in nature.
+For each, we will first introduce the formal structure in some detail and then discuss the account according to our established criteria.
 We mostly follow \textcite{yalcin10_probab_operat} and \textcite{holliday13_measur} in our exposition.
@@
 
-\section{The Epistemic Modal \emph{probable}}
+\subsection{Epistemic Modals}
+
+In this subsection, we briefly introduce epistemic modals and the propositional language we are going to study \emph{probable}-talk in.
+
 Epistemic modals are ubiquitous in everyday conversation.
@@
 This is what we'll adopt here, too.
-There are a host of interesting philosophical and linguistic problems associated with uttering sentences involving epistemic modals (cf.
+There are a host of interesting philosophical and linguistic issues associated with uttering sentences involving epistemic modals (cf.
 \cite{yalcin07_epist_modal}), which will mostly not be the focus of this paper.
-Rather, we will concern ourselves with analyzing \emph{probable}.
-The epistemic modal \emph{probable} is more nuanced and is subject to grading:
+Rather, we will concern ourselves with analyzing the modal \emph{probable}, which is more nuanced and subject to grading:
 something can reasonably be judged more or less probable. It comes in comparative (e.g. `$\varphi$ is at least as likely as $\psi$') and absolute (e.g. `probably $\varphi$') flavor.
@@
 
-To base the following discussions on a common language, we define a propositional language $\L$ (cf. \cite{harrison-trainor17_prefer}):
+To base the following discussions across different accounts on a common language, we define a propositional language $\L$ (cf. \cite{harrison-trainor17_prefer}):
 \[
-\varphi ::= p ~|~ \neg \varphi ~|~ (\varphi \land \psi) ~|~  (\varphi \succeq \psi) ~|~ \triangle\varphi 
+\varphi ::= p ~|~ \neg \varphi ~|~ (\varphi \land \varphi) ~|~  (\varphi \succeq \varphi) ~|~ \triangle\varphi 
 \]
-Where $p$ is an atomic formula, i.e. $p \in \text{Atom}$. The other boolean connectives $(\varphi \rightarrow \psi), (\varphi \vee
-\psi)$ as well as $\top, \bot$ are defined in the standard way from negation and conjunction.
+Where $p$ is an atomic formula, i.e. $p \in \texttt{Atom}$. The other boolean connectives $\rightarrow, \vee$ as well as $\top, \bot$ are defined in the standard way from negation and conjunction.
 The intended readings are as follows:
@@
 
-\subsection{Criteria for Adequacy}
+\section{Adequacy Criteria}
+In this section, we discuss criteria for an adequate analysis of \emph{probable}-talk we are employing in this paper, and survey additional criteria we did not include in the evaluation.
+
 In his \parencite*{yalcin10_probab_operat}, Yalcin critically evaluates Kratzer's relative likelihood account and also Hamblin's account, which is based on the notion of possiblity (resp.
@@
 Yalcin does this by following the good philosophical practice of establishing a set of desiderata the accounts can be evaluated against.
-In the case for judging semantics for a natural language phenomenon, these naturally come in the form of inference patterns that strike one as intuitively valid or invalid.
+In the case for judging semantics for a natural language phenomenon, these naturally come in the form of inference patterns that strike one as intuitively valid or not.
 The practice is fruitful because it gives criteria to compare different accounts in a transparent and comprehensible fashion, and shifts the focus of the problematic notion of \emph{intuitive plausibility} from judging the accounts themselves to judging the plausibility of the inference patterns.
-Whether some formally specified semantics validates a given inference pattern is then simply not a matter of debate and can be shown mathematically given the assumptions one is forced to make explicit.
-The rules are not meant to characterize a logic, of course. Let us briefly go through all criteria we evaluate the accounts by in this paper.
-The criteria are stated in the form of inference patterns. The inferences here can just be understood as classical truth preservation.
+Whether some formally specified semantics validates a given inference pattern is then simply not a matter of debate and can be shown mathematically, given the assumptions one is forced to make explicit.
+The rules are not meant to characterize a logic, of course. In this paper, we are not concerned with proving theorems about a logic at all.
+
+Let us briefly go through all criteria we evaluate the accounts by in this paper.
+The criteria are stated in the form of inference patterns.
+The inferences here can just be understood as classical truth preservation.
 
@@
 
-What do we mean by \emph{valid} in the following? We refer here to intuitively reasonable inference patterns. We ascribe a competent speaker of English to agree in validating or rejecting a pattern.
+What do we mean by \emph{valid} in the following? We refer here to intuitively reasonable inference patterns. We assume a competent speaker of English to agree in validating or rejecting a pattern.
 
-Patterns (V1-V5) are clearly valid:
 Intuitively, it's clear that not both a proposition and its negation should be considered probable, expressed in (V1).
@@
 
-\noindent The concluding three patterns are intuitively invalid. Yalcin offers the following counterexample to (I1) when throwing a coin, which is clearly problematic.
+\noindent The concluding three patterns are intuitively \emph{invalid}. Yalcin offers the following counterexample to (I1) when throwing a coin, which is clearly problematic.
 \begin{quote}
@@
 
-(I2) and (I3) are even more obviously undesirable. But some semantics, as we will see, still validate these patterns.
+\noindent (I2) and (I3) are even more obviously undesirable. But some semantics, as we will see, still validate these patterns.
 
@@
 It might be the case that speakers use it `innocently' without recourse to probability theory, but it's a different question of whether they do so competently.
-We argue that they might as well don't.
+We argue that they might as well not.
 The result is that the criterion does not necessarily help us evaluate adequate semantics for likelihood talk, and thus will be excluded from the present considerations.
 
-Yalcin also discuss criteria concerning the combination of epistemic modals and indicative conditionals (V8-V10, not listed here).
-While undoubtedly very interesting, also considering semantics for conditionals and integrating those with epistemic modal semantics would be beyond the scope of this short paper.
+Yalcin also discusses criteria concerning the combination of epistemic modals and indicative conditionals (V8-V10, not listed here).
+While undoubtedly very interesting, also considering semantics for conditionals and integrating those with epistemic modal semantics would go beyond the scope of this short paper.
 
@@
 
-Kratzer postulates that modality is always relative to a certain kind of interpreting the modalities involved.
-She sets out to formulate these different modalities in a common framework such that we'd only need to specify some parameters of the framework to determine the relevant modalities and give truth conditions for sentences involving modalities, while focusing on epistemic modals.
+Kratzer postulates that modality is always relative to a certain kind of interpretation of the modalities involved.
+She sets out to formulate these different modalities in a common framework such that we'd only need to specify some parameters of the framework to determine the relevant modalities and to give truth conditions for sentences involving modalities.
 
 Kratzer is unhappy with what she calls the \emph{standard analysis} as it gives the wrong verdict in two salient scenarios.
-These are concerned with conflicting rules of law and an a combination of indicative conditionals and modals, respectively.
+These are concerned with conflicting rules of law and a combination of indicative conditionals and modals, respectively.
 We will not reiterate these scenarios here, but--spoiler alert--Kratzer's theory manages to do them justice.
 
-More relevantly, the account for modality according to Kratzer needs to include graded modalities, of the following sort:
+More relevantly, an account for modality according to Kratzer needs to include graded modalities, of the following sort:
 \begin{enumerate}[nosep,label=\alph*)]
@@
 Here, the modalities are listed in decreasing strength, such that the intended reading is that a) implies b), b) implies c), and c) implies d).
-Note that is a qualitative approach to graded modals, as opposed to quantitative approaches. Some of these employ a scale structure in the semantics, as described by \textcite{lassiter10_gradab}.
 
@@
 In addition, we'd have semantics for epistemic modals and \emph{probable}-talk that do not need to make recourse to probability theory.
-Whether these two features actually do speak in favor of Kratzer's account shall not be evaluated in this paper and are just now mentioned.
+Whether these two features actually do speak in favor of Kratzer's account shall not be evaluated in this paper and are now just mentioned.
 We stick to the criteria defined in the beginning.
@@
 How do the semantics look like?
-We assume a set $W$ of possible worlds, propositions are subsets of $W$, and assume that a proposition $p$ is true at $w$ iff $w \in p$.
-The crucial element in Kratzer's semantics that distinguishes her account from most simple semantics via Kripke frames with only a single accessibility relation is the \emph{conversational background}.
+We assume a set $W$ of possible worlds, propositions are subsets of $W$, and assume that a proposition $A$ is true at $w$ iff $w \in A$.
+The crucial element in Kratzer's semantics that distinguishes her account from the \emph{standard analysis} is the \emph{conversational background}.
 It has two components.
@@
 From this, Kratzer defines a the semantics for a list of different expressions, like `good possibility', `possibility' and so on.
-For our purposes, it suffices to look at the following ordering on propositions:
+For our purposes, it suffices to look at the following ordering on propositions.
 
 The induced ordering on worlds $\leq_{g(w)}$ is `lifted' to an ordering on the level of propositions.
-For a modal base $f$ and a ordering source $g$, for propositions $A,B$ and world $w$, we can define
+For a modal base $f$ and an ordering source $g$, for propositions $A,B$ and world $w$, we can define
 \begin{equation}
@@
 \renewcommand\labelitemi{--}
-      \item $W$ is a non-empty set of possible worlds,
+      \item $W$ is a finite, non-empty set of possible worlds,
       \item $f,g$ are functions $f,g: W \rightarrow \wp(W)$,
-      \item $V$ is a function $V: \text{Atom} \rightarrow \wp(W)$
+      \item $V$ is a function $V: \texttt{Atom} \rightarrow \wp(W)$
     \end{itemize}
@@
     \begin{enumerate}[nosep]
-      \item If $p \in \text{Atom}$, $M,w \models p$ iff $w \in V(p)$,
+      \item If $p \in \texttt{Atom}$, $M,w \models p$ iff $w \in V(p)$,
       \item $M,w \models \neg \varphi$ iff $M,w \not\models \varphi$
@@
 
-Kratzer's account does \emph{not} validate (V11-V12). \textcite[pp.~935, note~8]{yalcin10_probab_operat} gives a countermodel.
+Kratzer's account does \emph{not} validate (V11-V12).
+\textcite[pp.~935, note~8]{yalcin10_probab_operat} gives a countermodel.\footnote{Which, however, requires an infinite $W$.
+We need to further look into this.}
 In addition, the account \emph{does} validate pattern (I1), as can easily be seen.
@@
 \section{Hamblin's Possibility Semantics}
-Already in the 1950's, \textcite{hamblin59_modal_probab} developed a semantics for the \emph{probable}-operator based on what he called plausibility and more recently is referred to as possiblity.
+Already in the 1950's, \textcite{hamblin59_modal_probab} developed a semantics for the \emph{probable}-operator based on what he called \emph{plausibility} and more recently is referred to as \emph{possiblity}.
 Possibility functions are quite similar to probability functions, but do not require finite additivity.
@@
 \subsection{Formal Setup}
-\noindent Let $W$ be a set. A boolean algebra on $W$ is a set $\F \subseteq \wp(W)$ such that
+\noindent Let $W$ be a set. A \emph{boolean algebra} on $W$ is a set $\F \subseteq \wp(W)$ such that
 \begin{enumerate}[nosep]
@@
 
-\noindent Let $\F$ be a boolean algebra. A possibility function is a function $p: \F \rightarrow [0,1]$ such that
+\noindent Let $\F$ be a boolean algebra. A \emph{possibility function} is a function $p: \F \rightarrow [0,1]$ such that
 \begin{enumerate}[nosep]
@@
         \renewcommand\labelitemi{--}
-      \item $W$ is a set of possible worlds,
+      \item $W$ is a finite, non-empty set of possible worlds,
       \item $R$ is a binary relation on $W$,
-        \item $V$ is a function $V: \text{Atom} \rightarrow \wp(W)$,
+        \item $V$ is a function $V: \texttt{Atom} \rightarrow \wp(W)$,
         \item $\mathcal{F}$ is a function assigning each world $w \in W$ a boolean algebra $\F_w$ on $R[w]$, and 
@@
 Further, Hamblin validates pattern (V11-V12) \parencite[][p.~926]{yalcin10_probab_operat}.
-Like Kratzer, though, Hamblin also validates (I1) and (I2), but more egregiously, even (I3): 
+Like Kratzer, though, Hamblin also validates (I1) and (I2), but more glaringly even (I3): 
 \begin{center}
@@
 Unsatisfied with the accounts described so far, Yalcin proposes to overcome the wariness towards probability functions as semantics for probability talk.
-The semantics developed by \textcite{yalcin10_probab_operat} and very similarly by \textcite{lassiter10_gradab} is the absolutely straightforward application of probability measures towards our present problem, so obvious in fact that it strikes me as noteworthy that these seem to be among the earliest applications of probability functions to \emph{probable}-talk, as both Yalcin and Lassiter claim.
+The semantics developed by \textcite{yalcin10_probab_operat} and very similarly by \textcite{lassiter10_gradab} is the straightforward application of probability measures towards our present problem, so obvious in fact that it strikes me as noteworthy that these seem to be among the earliest applications of probability functions to \emph{probable}-talk, as both Yalcin and Lassiter claim.
 The following definitions are quite unsurprising, then.
@@
   \item $\mu(W) = 1$
-  \item $\mu(U \cup V) = \mu(U) + \mu(V) \text{ if } U \cup V = \emptyset $
+  \item $\mu(U \cup V) = \mu(U) + \mu(V) \text{ if } U \cap V = \emptyset $
 \end{enumerate}
@@
       \item $M,w \models \varphi \succeq \psi$ iff $\mu_w(\lb \varphi \rb^M) \geq \mu_w(\lb \psi \rb^M) $,
-      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ^{M,w} \neg \varphi$ iff $ \mu_w(\lb \varphi \rb^M) > .5$, and
+      \item $M,w \models \triangle \varphi$ iff $M,w \models \varphi \succ^{M,w} \neg \varphi$ iff $ \mu_w(\lb \varphi \rb^M) > .5$
     \end{enumerate}
@@
 Let's look at some of them. 
-To compare, the probability semantics validate V2: Suppose $M,w \models
+The probability semantics validate V2: Suppose $M,w \models
 \triangle(\varphi \land \psi)$. Then $\mu_w(\lb \varphi \land \psi\rb^M) > .5$.
@@
 \noindent To see this, fix a model $M$ and a world $w \in W$ (sub- and superscripts suppressed).
-Let $\mu(\lb\varphi\rb) = .6;~ \lb\psi\rb \cap \lb\chi\rb=\emptyset;~ \mu(\lb\psi\rb) = \mu(\lb\chi\rb) = .4$. (that such a model exists can be easily verified).
+Let $\mu(\lb\varphi\rb) = .6;~ \lb\psi\rb \cap \lb\chi\rb=\emptyset;~ \mu(\lb\psi\rb) = \mu(\lb\chi\rb) = .4$ (that such a model exists can be easily verified).
 Then $\mu(\lb \psi \rb \cup \lb \chi \rb) = .8$.
@@
 \emph{probable}-talk semantics?
-Not quite, as we will see in the next section.
+No, as we will see in the next section.
 
@@
 It could be worthwile to investigate further where this discrepancy is coming from.}
-They also briefly consider an ordering directly on the set of propositions instead of inducing the order from an order on worlds, and state that here, one can quite straightforwardly constrain the ordering such that it provides a semantic to satisfy the adequacy criteria \parencite[p.~924]{holliday13_measur}.
+They also briefly consider an ordering directly on the set of propositions instead of inducing the order from an order on worlds, and state that here, one can quite straightforwardly constrain the ordering such that it provides semantics which satisfy the adequacy criteria \parencite[p.~924]{holliday13_measur}.
 They dismiss it, however, because it is more desirable to not have a primitive order on propositions.
-It seems they are themselves doubting this point and merely reiterate an established point.\footnote{This, too, seems worth investigating further.}
+It seems they are themselves doubting this claim and merely reiterate an established point.\footnote{This, too, seems worth investigating further.}
 
@@
 For example, while Kratzer's lifting creates a total ordering on propositions if the order on worlds is total, not so for Holliday and Icard's lifting (cf.
-\parencite[][p.~525]{holliday13_measur} for a nice extended argument for why this is desirable).
+\textcite[][p.~525]{holliday13_measur} for a nice extended argument for why this is desirable).
 We describe the precise change in the next section, and have a look at the results concerning our criteria after that.
@@
         \renewcommand\labelitemi{--}
-      \item $W$ is a set of possible worlds,
+      \item $W$ is a finite, non-empty set of possible worlds,
       \item $R$ is a binary relation on $W$,
-      \item $V$ is a function $V: \text{ Atom } \rightarrow \wp(W)$, and
+      \item $V$ is a function $V: \texttt{ Atom } \rightarrow \wp(W)$, and
       \item $\succeq$ is a function assigning each world $w \in W$ a preorder
@@
 \end{definition}
-For any proposition $P \subseteq W$, $P_w := P \cap R[w]$. Further, for two proposition $A,B \subseteq W$ we define
+For any proposition $P \subseteq W$, $P_w := P \cap R[w]$. Further, for two propositions $A,B \subseteq W$ we define
 \begin{multline}
@@
       W,R,V,\succeq \rangle}$, $w \in W, \varphi,\psi \in \L$ and let $\succeq^{M,w}$ be the order on $W$ defined by Equation \ref{eq:injection}.
-We the define clauses 1-6 just like in Kratzer preferential semantics (Definition \ref{def:kratsem}).
+We define clauses 1-6 just like in Kratzer preferential semantics (Definition \ref{def:kratsem}).
 \end{definition}
@@
 Holliday and Icard's semantics is very similar to Kratzer's.
-In particular, we can associate the modal base and ordering source of Kratzer's with the binary relation $R$ and the $\geq$-function.
+In particular, we can associate the modal base and ordering source of Kratzer's with the binary relation $R$ and the $\succeq$-function.
 Just as the modal base determines for each world a set of epistemically accessible worlds, so does $R[w]$.
-And just as the ordering source induces an order on propositions, so does $\geq$.
-For our present purposes, both formulations are equivalent even.
-Holliday and Icard make a crucial change to how the order is induced, however.
-To see this, note that Equation \ref{eq:lifted} can be rewritten as an equivalent definition:
+And just as the ordering source induces an order on propositions, so does $\succeq$.
+For our present purposes, both formulations are equivalent.
+However, Holliday and Icard make a crucial change to how the order is induced.
+To see this, note that Equation \ref{eq:lifted} can be rewritten equivalently:
 
-For a modal base $f$ and a ordering source $g$, for propositions $A,B$ and world $w$, define
+For a modal base $f$ and a ordering source $g$, for propositions $A,B$ and a world $w$, define
 \begin{multline}
@@
 \end{multline}
-Compared to Equation \ref{eq:injection}, besides the inverted direction of $\geq$ which is just due to how the notions were defined, the difference is that Holliday and Icard require an injective function assigning each element of $B$ a unique element of $A$ such that the element of $A$ is more plausible, normal etc.
+Compared to Equation \ref{eq:injection}, besides the inverted direction of $\geq$ which is just due to how the notions were defined, the difference is that Holliday and Icard require an \emph{injective} function assigning each element of $B$ a unique element of $A$.
 This simple change has interesting consequences, as we will see in the next section. 
@@
 
-Fix a model $M$ and a world $w$.
-Let $W = \{abcd\}$, ordered by $M$ like so: $a > b > c > d$.
-Let $A = \{ab\}, B = \{bc\}, C = \{cd\}$.
-It's easy to see that by (\ref{eq:injection}), we have $A \succ B \succ C$.
-However, we do not have $A \succ (B \cup C)$, since we can't construct an injection like required.
-Hence, (I1) is not validated.
-A clear improvement over Kratzer's semantics.
+Fix a model $M$ and a world $w$. Let $W = \{abcd\}$, ordered by $M$ like so: $a
+> b > c > d$. Let $A = \{ab\}, B = \{bc\}, C = \{cd\}$. It's easy to see that by
+(\ref{eq:injection}), we have $A \succ B \succ C$. However, we do not have $A
+\succ (B \cup C)$, since we can't construct an injection like required. Hence,
+(I1) is not validated. And neither are (I2) and (I3). A clear improvement over
+Kratzer's semantics.
+
+This concludes our discussion. Next, we'll briefly review what we have achieved
+so far and give an outlook on the direction for future studies.
 
 \section{Conclusion}
-\begin{figure}
+In this paper, we compared different accounts for semantics of \emph{probable}-talk.
+The criteria we established were not all satisfied by Kratzer's or Hamblin's account.
+Since Yalcin's (and also Lassiter's) probability semantics satisfy all criteria, it looked like the debate between preferential and probabilistic or qualitative and quantitative semantics had been settled.
+But Holliday and Icard improved on Kratzer's account such that it, too, satisfied the criteria.
+Thus at least from this vantage point, both types of semantics are able to make valuable contributions to explaining what we mean by \emph{probable}.
+A summarizing overview is provided in Figure \ref{fig:table}.
+
+\begin{figure}[ht]
 \begin{center}
@@
 \end{figure}
-In this paper, we compared different accounts for semantics of
-\emph{probable}-talk. The criteria we established were not satisfied by
-Kratzer's or Hamblin's account. Since Yalcin's (and also Lassiter's) probability
-semantics satisfy all criteria, it looked like the debate between preferential
-and probabilistic or qualitative and quantitative semantics had been settled
-with regards to the criteria. But Holliday and Icard improved on Kratzer's
-account such that it, too, satisfied the criteria. Thus at least from this
-vantage point, both types of semantics are able to make valuable contributions
-to explaining what we mean by \emph{probable}. An summarizing overview is
-provided in Figure \ref{fig:table}.
 
-Of course, this paper only scratches the surface of this topic. First, we
-severely limited the choice of criteria. Much more can be said as to how
-\emph{probable}-talk interfaces with other modals like \emph{might} or
-\emph{must}, or with indicative conditionals. We did not address the related
-discussion of graded modals and semantics on a scale like in Kennedy 2007 (look
-up reference in Lassiter). What's more, there is a host of interesting further
-work by \textcite{holliday13_measur} and \textcite{harrison-trainor17_prefer} ...
-\todo{Finish this section}
+Of course, this paper only scratches the surface of this topic.
+First, we severely limited the choice of criteria.
+Much more can be said as to how \emph{probable}-talk interfaces with other modals like \emph{might} or \emph{must}, or with indicative conditionals.
+We did not address the related discussion of graded modals and semantics on a scale like in Kennedy 2007 (look up reference in Lassiter).
+Additionally, nested modal formulae of the form ($\varphi \succeq (\psi \succeq \chi)$) are allowed by the syntax but have not been evaluated in this paper.
+We have only looked at finite $W$. There certainly are important additional issues to consider when $W$ can have any cardinality.
+
+There is very interesting further work by \textcite{holliday13_measur} and \textcite{harrison-trainor17_prefer} concerned with developing logics for the different semantics.
+In particular, they present a type of preferential semantics very similar to the one presented here
+and a probability semantics also very similar to the one presented here generalized to imprecise probabilities.
+They then show that both are sound and complete with respect to the same set of axioms.
+Their result hints at deep structural similarities.
+It should prove very interesting to work out connections to the \emph{probable}-talk semantics.
 
